### 2016-08-02 manuscript.tex
First commit of AAS paper

\documentclass[]{aiaa-tc}% insert '[draft]' option to show overfull boxes

\usepackage{aiaa_packages}

 \title{Low-Thrust Trajectory Design Near Asteroids Using Invariant Manifolds and Reachability Sets}

 \author{
  Shankar Kulumani\thanksibid{1}%
    \thanks{Doctoral Student, \href{mailto:skulumani@gwu.edu}{skulumani@gwu.edu}. Student AIAA Member.}
  \ and Taeyoung Lee\thanksibid{2}\thanks{Associate Professor, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}. AIAA Member}\\
  {\normalsize\itshape
   Mechanical and Aerospace Engineering, George Washington University, 800 22nd St NW, Washington DC }\\
   }

 % Data used by 'handcarry' option if invoked
 \AIAApapernumber{YEAR-NUMBER}
 \AIAAconference{Conference Name, Date, and Location}
 \AIAAcopyright{\AIAAcopyrightD{YEAR}}

\begin{document}

\maketitle

\begin{abstract}
Abstract
\end{abstract}

\section*{Nomenclature}

\begin{tabbing}
  XXX \= \kill% this line sets tab stop and adds a newline
  $J$ \> Jacobian Matrix \\
  $f$ \> Residual value vector \\
  $x$ \> Variable value vector \\
  $F$ \> Force, \si{\newton} \\
  $m$ \> Mass, \si{\kilo\gram} \\
  $\Delta x$ \> Variable displacement vector \\
  $\alpha$ \> Acceleration, \si{\meter\per\second\squared} \\[5pt]
  \textit{Subscript}\\
  $i$ \> Variable number \\
\end{tabbing}

\section{Introduction}

% Motivation for missions/studying asteroids
Small solar system bodies, such as asteroids and comets, are of significant interest to the scientific community.
These small bodies offer great insight into the early formation of the solar system.
This insight offers additional detail into the formation of the Earth and also the probable formation of other planetary systems.
Of particular interest are those near-Earth asteroids (NEA) which inhabit heliocentric orbits in vicinity of the Earth.
These easily accessible bodies provide attractive targets to support space industrialization, mining operations, and scientific missions..
NEAs potentially contain many materials useful for propulsion, construction, semiconductors, precious and strategic metals~\cite{ross2001}.
In addition, these NEAs are also of concern for their potential to impact the Earth~\cite{wie2008}.
Asteroids and comets are the greatest threat to future civilizations and as a result there is a focused effort to mitigate these risks.
Operating in the vicinity of asteroids is a challenging problem for spacecraft missions.

% Difficulty in system model 
While there has been significant study of interplanetary transfer trajectories, relatively less analysis has been conducted on operations in the vicinity of asteroids.
The dynamic environment of around asteroids is strongly perturbed and challenging for analysis.
A combination of factors contribute to make operations in the vicinity of small bodies challenging, such as distended body shapes, unknown spin states, and non-gravitational effects such as solar radiation pressure~\cite{scheeres2012}.

% most use a spherical harmonic model but we use a polyhedron model

% Investigate low thrust propulstion for manuevers
% vesta paper
% gravity tractor papers

%Reachability set is key to the design of transfers

\section{System Model}

\subsection{Polyhedron Gravity Model}

Cite the original werner papers

\subsection{Asteroid Dynamics}
Cite scheeres and his book

Equations of motion

Jacobi constant

Relate to three body problem

Equilibrium points. Cite work done with triaxial ellipsoids and other Castalia papers

Periodic orbits

\section{Reachability Set}

Show \Poincare section

Optimal control problem

Discuss the constraints and angles on the four dimensional space of the section

Show partial derivatives

\section{Numerical Simulation}

Transfer about asteroid Castalia - cite some Scheeres papers

\section{Conclusion}

\section*{Appendix}

\section*{Acknowledgments}

A place to recognize others.

\bibliographystyle{aiaa} 
\bibliography{library}

\end{document}

### 2016-08-03 manuscript.tex
Add detail to intro and polyhedron equations

@@
 \begin{abstract}
-Abstract
+Write an awesome abstract
+
+Use the reachability set to compute transfers
+
+extend work already done in three body problem to motion around asteroid
+
+Numerical example for asteroid 4769 Castalia
 \end{abstract}
@@
 Asteroids and comets are the greatest threat to future civilizations and as a result there is a focused effort to mitigate these risks.
-Operating in the vicinity of asteroids is a challenging problem for spacecraft missions.
+In spite of the great interest in asteroids, the operation of spacecraft in thier vicinity is a challenging problem.
 
@@
 While there has been significant study of interplanetary transfer trajectories, relatively less analysis has been conducted on operations in the vicinity of asteroids.
-The dynamic environment of around asteroids is strongly perturbed and challenging for analysis.
-A combination of factors contribute to make operations in the vicinity of small bodies challenging, such as distended body shapes, unknown spin states, and non-gravitational effects such as solar radiation pressure~\cite{scheeres2012}.
+The dynamic environment of around asteroids is strongly perturbed and challenging for analysis and mission operation.
+Due to their small size and therefore low gravitational attraction asteroids have irregular shapes and potentially chaotic spin states.
+Furthermore, due to the low gravitational attraction, other non-gravitional effects, such as solar radiation pressure, become more significant.
+The orbital enviornment is in general quite complex and analytical insights are difficult to generate.
 
-% most use a spherical harmonic model but we use a polyhedron model
+% Must estimate gravity and shape from ground based optical measurements
+% most use a spherical harmonic model or a ellipsoid model but we use a polyhedron model
+An accurate gravitional potential model is neccessary for the operation of spacecraft about asteroids.
+Additionally, a detailed shape model of the asteroid is needed for trajectories passing close to the body.
+The classic approach is to expand the gravitational potential into a harmonic series and compute the series coefficients.
+Radio tracking data of an orbiting spacecraft allows one to estimate the series coefficients.
+The harmonic representation are guaranteed to converge outside of the circumscribing sphere and can be truncated at a finite order based on accuracy requirements.
+However, the harmonic expansion is always an approximation as a result of the infinite order series used in the representation.
+Additionally, the harmonic model used outside of the circumscribing sphere is not guaranteed to converge inside the sphere.
+As a result, additional steps must be taken to determine a valid harmonic expansion for particles close to the body. 
+This results in a cumbersome gravity field model that requires additional constraints to ensure continuity and validity at the radius of the circumscribing sphere~\cite{werner1996}.
+Instead, we model the asteroid as a constant-density polyhedron and avoid the issues of the harmonic expansion while enabling several other useful advantages.
 
-% Investigate low thrust propulstion for manuevers
-% vesta paper
-% gravity tractor papers
+% benefits of the polyhedron model
+A polyhedral model of the surface of an asteroid can be determined from remote optical or radar sensors.
+The faces of the polyhedron can be large or small and allows for fine detail such as depression, craters, ridges, or interior voids. 
+In addition, there is no requirement for the body to be modeled at a uniformly high resolution so small details can be incorprated with minimal cost.
+From the shape model, an analytical, closed form expression for the gravitational potential can be derived.
+The polyhedral approach provides an accurate gravitational model consistent with the resolution of the shape and the chosen discretization.
+Furthermore, the polyhedron model is an exact solution up to the surface of the body. 
+Therefore, this model is ideal for missions traversing large region both close and far from the asteroid.
 
-%Reachability set is key to the design of transfers
+% similarity to the three body problem
+The irregular shape of asteroids leads to a richer dynamics as compard to the familar Kepler's problem, which is based on a point mass assumption.
+The motion of particles around asteroids is modeled using the restricted full two-body problem. 
+This model has many similarities with the restricted three body problem, and much of the theory developed there is also applicable.
+There has been much work in characterizing the relative equilibria and periodic orbits in the three-body problem.
+In addition, orbital transfers have been designed which exploit the invariant manifolds of the three-body problem for low-energy manuevers~\cite{mingotti2011,grebow2011}.
+The similarity of the three-body problem to motion around astreroids allows for much of the same theory to be applied to the asteroid problem.
+More recently, the invariant manifolds around asteroids have been proposed for orbital transfers and landing manuevers~\cite{mondelo2010,herrera2014}.
 
-\section{System Model}
+% use of low thrust propulsion
 
+The application of optimal control methods for orbital trajectory design is nontrivial.
+In order to implement any optimization method a sufficiently accurate ``initial guess'' is required.
+Frequently, insight into the problem or intuition on the part of the designer is often required to determine initial conditions that will converge to the optimal solution.
+However, the asteroid system dynamics are nonlinear and exhibit chaotic behaviors. 
+This makes solving the optimization problem highly dependent on the initial condition.
+Similar to the three-body problem, there is an insufficient number of analytical constants to derive an analytical solution in general. 
+As a result, accurate numerical methods are required to determine optimal solutions.
+These methods are critically dependent on accurate initial guess in order to allow for convergence to an optimal solution.
+
+% SYSTEMATIC DESIGN TO AVOID DIFFICULTIES IN CHOOSING A GOOD INITIAL GUESS
+% CAPTURE LONG TERM EFFECTS OF LOW THRUST ACCURATELY IN NUMERICAL SIMULATION
+In this paper, we extend the design method developed in the three-body problem to motion about asteroids~\cite{kulumani2015}.
+Our approach avoids the difficulties in selecting an appropriate initial guess for optimization.
+Instead, we utilize the concept of the reachability set to enable a simple methodology of selecting initial conditions to achieve general orbital transfers. 
+Given an initial condition and fixed time horizon, the reachable set is the set of states attainable, subject to the operational constraints of the spacecraft. 
+In addition, the generation of the reachable set allows for a more systematic method of determining initial conditions and eases the burden on the designer.
+This simple methodology allows for extended transfer trajectories which iteratively approach a desired target orbit.
+
+\section{Asteroid Model}
+
+\subsection{Shape Model}
+Cite location of shape model database
+
+Cite Scheeres orbits close to 4769 Castalia
 \subsection{Polyhedron Gravity Model}
+
+The gravitational attraction due to a constant density polyhedron is given as
+\begin{align*}
+	U(\vecbf{r}) &= 1\frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f
+\end{align*}
+where \( \vecbf{r}_e, \vecbf{r}_f \) is the vector from the spacecraft to any point on the respective edge or face.
+The polyhedron is defined by an array of vectors in the body fixed frame which define the vertices of the body.
+Triangular faces are defined as the plane created by any three vertices. 
+Consider three vectors \( \vecbf{v}_0, \vecbf{v}_1, \vecbf{v}_2 \), assumed to be ordered in a counterclockwise direction, which define a face. 
+The outward normal vector to the face and to each edge is defined as
+\begin{align*}
+	\hat{\vecbf{n}}_f &= \parenth{\vecbf{v}_{1} - \vecbf{v}_0} \times \parenth{\vecbf{v}_{2} - \vecbf{v}_1} ,\\
+	\hat{\vecbf{n}}_{e} &= \parenth{\vecbf{v}_{i+1} - \vecbf{v}_i} \times \hat{\vecbf{n}}_f .
+\end{align*}
+Using these normal vectors we define two dyads
+\begin{align*}
+	\vecbf{E}_e &= \hat{\vecbf{n}}_A \hat{\vecbf{n}}_{12}^A + \hat{\vecbf{n}}_B \hat{\vecbf{n}}_{21}^B ,\\
+	\vecbf{F}_f &= \hat{\vecbf{n}}_f \hat{\vecbf{n}}_f .
+\end{align*}
+The edge dyad \( \vecbf{E}_e \) is defined for each edge and a function of the two adjacent faces meeting at the edge. 
+The face dyad \( \vecbf{F}_f \) is defined for each face and is a function of the face normal vector.
+
+Let \( \vecbf{r}_i \) be the vector from the spacecraft to the vertex \( \vecbf{v}_i \) and it's length is \( r_i = \norm{\vecbf{r}_i} \).
+The per-edge factor \( L_e \), for the edge connecting vertices \( \vecbf{v}_i \) and \( \vecbf{v}_j \), with a constant length \( e_{ij} \) is 
+\begin{align*}
+	L_e &= \ln \frac{r_i + r_j + e_{ij}}{r_i + r_j - e_{ij}}.
+\end{align*}
+
+For the face defined by the vertices \( \vecbf{v}_i, \vecbf{v}_j, \vecbf{v}_k \) the per-face factor \( \omega_f \) is
+\begin{align*}
+	\omega_f &= 2 \arctan \frac{\vecbf{r}_i \cdot \vecbf{r}_j \times \vecbf{r}_k}{r_i r_j r_k + r_i \parenth{\vecbf{r}_j \cdot \vecbf{r}_k} + r_j \parenth{\vecbf{r}_k \cdot \vecbf{r}_i} + r_k \parenth{\vecbf{r}_i \cdot \vecbf{r}_j}} .
+\end{align*}
+
+Using these definitions, the attraction, gravity gradient matrix, and Laplacian are defined as
+\begin{align*}
+	\nabla U ( \vecbf{r} ) &= -G \sigma \sum_{e \in \text{edges}} \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e + G \sigma \sum_{f \in \text{faces}} \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f ,\\
+	\nabla \nabla U ( \vecbf{r} ) &= G \sigma \sum_{e \in \text{edges}} \vecbf{E}_e  \cdot L_e - G \sigma \sum_{f \in \text{faces}} \vecbf{F}_f \cdot \omega_f , \\
+	\nabla^2 U &= -G \sigma \sum_{f \in \text{faces}}  \omega_f .
+\end{align*}
+
+One interesting thing to note is that both \( \vecbf{E}, \vecbf{F} \) can be precomputed without knowledge of the position of the satellite. 
+They are both solely functions of the vertices and edges of the polyhedral shape model.
+One a position vector \( \vecbf{r} \) is defined then the scalars \( \omega_f, L_e \) can be computed for each face and edge.
+
+Duplicate the equations for polyhedron model
+
+Give an outline of how to compute the potential (which equations and order)
 
@@
 
-\subsection{Asteroid Dynamics}
+\subsection{Spacecraft Equations of Motion}
 Cite scheeres and his book
@@
 
-Relate to three body problem
+Zero velocity curves
 
@@
 \section{Reachability Set}
+
+\subsection{Optimal Control Formulation}
 
@@
 
+Plots of \Poincare section
+
+Full trajectory plots
+
 \section{Conclusion}
-
-\section*{Appendix}
 

### 2016-08-04 manuscript.tex
Starting on equations of motion

@@
 
- \title{Low-Thrust Trajectory Design Near Asteroids Using Invariant Manifolds and Reachability Sets}
+ \title{Low-Thrust Trajectory Design Near Asteroids Using Reachability Sets}
 
@@
 Cite Scheeres orbits close to 4769 Castalia
+
+Assuming constant rotation rate for asteroid
+
 \subsection{Polyhedron Gravity Model}
@@
 \subsection{Spacecraft Equations of Motion}
+
+The motion of a massless particle, or spacecraft, about an asteroid shares many similarities with that of the three-body problem.
+As is typical in the three-body problem, the equations of motion are usually represented in a uniformly rotating frame aligned with the two primaries.
+Similarily, the equations of motion about an asteroid are also defined in a body-fixed frame with uniform rotation.
+In this reference frame, the gravitational potential field is time invariant and only a function of the position of the particle.
+In addition, since the rotational rate of the asteroid is constant the equations of motion are time invariant.
+Finally, the use of the rotating reference frame allows for much greater insight into the dynamic structure of the behavior around the asteroid.
+
+We define a reference frame originating at the center of mass of the asteroid.
+
 Cite scheeres and his book
@@
 
-Periodic orbits
+\subsection{Determining Periodic Orbits}
 
-\section{Reachability Set}
+Periodic orbit computation summary. Cite Scheeres 2000 (Evaluation of the Dynamic environment of an asteroid)
+
+\section{Reachability Set on \Poincare Section}
+Define reachability set
+
+Define \Poincare section
 
@@
 
-Show \Poincare section
-
-Optimal control problem
+Formulate OCP to generate the reachability set
 
 Discuss the constraints and angles on the four dimensional space of the section
-
-Show partial derivatives
 
@@
 Full trajectory plots
+
+Thruster magnitude is chosen to emulate some real thrusters - cite the Dawn paper
 

### 2016-08-05 manuscript.tex
Correct error in aiaa_packages.sty
Continue adding detail on eoms

@@
 We define a reference frame originating at the center of mass of the asteroid.
+The body-fixed reference frame is composed of the unit vectors \( \hat{\vecbf{x}} , \hat{\vecbf{y}}, \hat{\vecbf{z}} \), which are aligned along the principal axes of smallest, intermediate, and largest moment of inertia, respectively.
+The body-fixed equations of motion of a massless particle about an arbitrarily rotating asteroid are given by
+\begin{align}\label{eq:body_eoms}
+	\ddot{\vecbf{r}} + 2 \vecbf{\Omega} \times \dot{\vecbf{r}} + \vecbf{\Omega} \times \parenth{ \vecbf{\Omega} \times \vecbf{r} } + \dot{\vecbf{\Omega}} \times \vecbf{r} = U_{\vecbf{r}} , 
+\end{align}
+where \( \vecbf{\Omega} \) is the instaneous angular velocity vector of the asteroid represented in the body-fixed frame, \( \vecbf{r} \) is the position of the particle in the body-fixed frame, and \( U_{\vecbf{r}} \) is the gradient of the gravitational potential~\cite{greenwood1988}.
+We assume that the asteroid rotates at a uniform rate, \( \norm{\vecbf{\Omega}} = \omega \), about the axis of the maximum moment of inertia, \( \vecbf{\Omega} = \omega \hat{\vecbf{z} }\).
+As a result, we can represent the equations of motion in scalar form as
+\begin{align} \label{eq:eoms}
+	\begin{split}
+    	\ddot{x} - 2 \omega \dot{y} - \omega^2 y &= U_x , \\
+    	\ddot{y} + 2 \omega \dot{x} - \omega^2 x &= U_y , \\
+    	\ddot{z} &= U_z .
+	\end{split}
+\end{align}
+
+We assume that in our problem we are modelling a spacecraft rather than a massless particle. 
+In this situation, the state is defined as \( \vecbf{x} = \begin{bmatrix}\vecbf{r} &\vecbf{v} \end{bmatrix}^T\) with \(\vecbf{r} = \begin{bmatrix} x & y & z \end{bmatrix}^T \in \R^{3\times1}\) and \(\vecbf{v}= \begin{bmatrix} \dot{x} & \dot{y} & \dot{z} \end{bmatrix}^T \in \R^{3\times1}\) representing the position and velocity with respect to the body-fixed frame, respectively.
+We further assume that our spacecraft is capable of exerting a translational force, \( \vecbf{u} \in \R^{3\times1} \), in any direction, while subject to a maximum magnitude constraint.
+This is typical of many spacecraft which offer full rotational freedom and can direct a maximum, and potentially varying, thrust in any direction.
+The equations of motion may be rewritten in state space form as
+\begin{align}\label{eq:state_space_eoms}
+	\begin{bmatrix} \dot{\vecbf{r}} \\ \dot{\vecbf{v}} \end{bmatrix} &=
+\end{align}
+where the matrix \( G \) represents the
 
 Cite scheeres and his book
-
-Equations of motion
 

### 2016-08-05 manuscript.tex
Adding more detail on dynamics and polyhedron model

@@
 
+Mention we're looking at asteroid 4769 Castalia
+
 \subsection{Polyhedron Gravity Model}
 
-The gravitational attraction due to a constant density polyhedron is given as
-\begin{align*}
-	U(\vecbf{r}) &= 1\frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f
-\end{align*}
-where \( \vecbf{r}_e, \vecbf{r}_f \) is the vector from the spacecraft to any point on the respective edge or face.
-The polyhedron is defined by an array of vectors in the body fixed frame which define the vertices of the body.
-Triangular faces are defined as the plane created by any three vertices. 
-Consider three vectors \( \vecbf{v}_0, \vecbf{v}_1, \vecbf{v}_2 \), assumed to be ordered in a counterclockwise direction, which define a face. 
-The outward normal vector to the face and to each edge is defined as
-\begin{align*}
-	\hat{\vecbf{n}}_f &= \parenth{\vecbf{v}_{1} - \vecbf{v}_0} \times \parenth{\vecbf{v}_{2} - \vecbf{v}_1} ,\\
-	\hat{\vecbf{n}}_{e} &= \parenth{\vecbf{v}_{i+1} - \vecbf{v}_i} \times \hat{\vecbf{n}}_f .
-\end{align*}
-Using these normal vectors we define two dyads
-\begin{align*}
-	\vecbf{E}_e &= \hat{\vecbf{n}}_A \hat{\vecbf{n}}_{12}^A + \hat{\vecbf{n}}_B \hat{\vecbf{n}}_{21}^B ,\\
+We represent the gravitational potential of the asteroid using a polyhedron gravitation model.
+This model is composed of a polyhedron, a three-dimensional solid body, which is defined by a series of vectors in the body-fixed frame.
+The vectors define vertices in the body-fixed frame as well as planar faces which compose the surface of the asteroid.
+We assume that each face is a triangle composed of three vertices and three edges.
+As a result, only two faces meet at each edge while three faces meet at each vertex. 
+Several asteroids have been accurately mapped from a combination of Earth based sensors as well as visiting spacecraft (CITE \href{http://sbn.psi.edu/pds/resource/rshape.html}{http://sbn.psi.edu/pds/resource/rshape.html}).
+Only the body-fixed vectors, and their associated topology, is required to define the exterior gravitational model.
+References~\citenum{werner1994} and~\citenum{werner1997} give a detailed derivation of the polyhedron model from first principles.
+Here, we summarize the key developments and equations required for implementation and clarity.
+
+Insert picture of face and vectors
+
+Consider three vectors \( \vecbf{v}_1, \vecbf{v}_2, \vecbf{v}_3 \), assumed to be ordered in a counterclockwise direction, which define a face. 
+It is easy to define the three edges of each face as
+\begin{align}\label{eq:edges}
+	\vecbf{e}_{i+1,i} = \vecbf{v}_{i+1} - \vecbf{v}_i ,
+\end{align}
+where the index \( i \in \parenth{1,2,3} \) is used to permute all edges of each face. 
+Since each edge is a member of two faces, there exist two edges which are defined in opposite directions between the same vertices.
+We can also define the outward normal vector to face \( f\)  as
+\begin{align}\label{eq:face_normal}
+	\hat{\vecbf{n}}_f &= \parenth{\vecbf{v}_{2} - \vecbf{v}_1} \times \parenth{\vecbf{v}_{3} - \vecbf{v}_2} ,
+\end{align}
+and the outward facing normal vector to each edge as
+\begin{align}\label{eq:edge_normal}
+	\hat{\vecbf{n}}_{i+1,i}^f &= \parenth{\vecbf{v}_{i+1} - \vecbf{v}_i} \times \hat{\vecbf{n}}_f .
+\end{align}
+For each face we define the face dyad \( \vecbf{F}_f \) as
+\begin{align}\label{eq:face_dyad}
 	\vecbf{F}_f &= \hat{\vecbf{n}}_f \hat{\vecbf{n}}_f .
-\end{align*}
+\end{align}
+Each edge is a member of two faces and has an outward pointing edge normal vector, given in~\cref{eq:edge_normal}, perpindicular to both the edge and the face normal.
+For the edge connecting the vectors \( \vecbf{v}_1 \) and \( \vecbf{v}_2 \) which are shared between the faces \(A\) and \( B\) the per edge dyad is given by
+\begin{align}\label{eq:edge_dyad}
+	\vecbf{E}_{12} = \hat{\vecbf{n}}_A \hat{\vecbf{n}}_{12}^A + \hat{\vecbf{n}}_B \hat{\vecbf{n}}_{21}^B .
+\end{align}
 The edge dyad \( \vecbf{E}_e \) is defined for each edge and a function of the two adjacent faces meeting at the edge. 
@@
 The per-edge factor \( L_e \), for the edge connecting vertices \( \vecbf{v}_i \) and \( \vecbf{v}_j \), with a constant length \( e_{ij} \) is 
-\begin{align*}
+\begin{align}\label{eq:edge_factor}
 	L_e &= \ln \frac{r_i + r_j + e_{ij}}{r_i + r_j - e_{ij}}.
-\end{align*}
+\end{align}
+For the face defined by the vertices \( \vecbf{v}_i, \vecbf{v}_j, \vecbf{v}_k \) the per-face factor \( \omega_f \) is
+\begin{align}\label{eq:face_factor}
+	\omega_f &= 2 \arctan \frac{\vecbf{r}_i \cdot \vecbf{r}_j \times \vecbf{r}_k}{r_i r_j r_k + r_i \parenth{\vecbf{r}_j \cdot \vecbf{r}_k} + r_j \parenth{\vecbf{r}_k \cdot \vecbf{r}_i} + r_k \parenth{\vecbf{r}_i \cdot \vecbf{r}_j}} .
+\end{align}
+The gravitational potential due to a constant density polyhedron is given as
+\begin{align}\label{eq:potential}
+	U(\vecbf{r}) &= 1\frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f
+\end{align}
+where \( \vecbf{r}_e, \vecbf{r}_f \) is the vector from the spacecraft to any point on the respective edge or face.
+Furthermore we can use these definitions to define the attraction, gravity gradient matrix, and Laplacian are defined as
+\begin{align}
+	\nabla U ( \vecbf{r} ) &= -G \sigma \sum_{e \in \text{edges}} \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e + G \sigma \sum_{f \in \text{faces}} \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f , \label{eq:attraction}\\
+	\nabla \nabla U ( \vecbf{r} ) &= G \sigma \sum_{e \in \text{edges}} \vecbf{E}_e  \cdot L_e - G \sigma \sum_{f \in \text{faces}} \vecbf{F}_f \cdot \omega_f , \label{eq:gradient_matrix}\\
+	\nabla^2 U &= -G \sigma \sum_{f \in \text{faces}}  \omega_f \label{eq:laplacian}.
+\end{align}
 
-For the face defined by the vertices \( \vecbf{v}_i, \vecbf{v}_j, \vecbf{v}_k \) the per-face factor \( \omega_f \) is
-\begin{align*}
-	\omega_f &= 2 \arctan \frac{\vecbf{r}_i \cdot \vecbf{r}_j \times \vecbf{r}_k}{r_i r_j r_k + r_i \parenth{\vecbf{r}_j \cdot \vecbf{r}_k} + r_j \parenth{\vecbf{r}_k \cdot \vecbf{r}_i} + r_k \parenth{\vecbf{r}_i \cdot \vecbf{r}_j}} .
-\end{align*}
-
-Using these definitions, the attraction, gravity gradient matrix, and Laplacian are defined as
-\begin{align*}
-	\nabla U ( \vecbf{r} ) &= -G \sigma \sum_{e \in \text{edges}} \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e + G \sigma \sum_{f \in \text{faces}} \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f ,\\
-	\nabla \nabla U ( \vecbf{r} ) &= G \sigma \sum_{e \in \text{edges}} \vecbf{E}_e  \cdot L_e - G \sigma \sum_{f \in \text{faces}} \vecbf{F}_f \cdot \omega_f , \\
-	\nabla^2 U &= -G \sigma \sum_{f \in \text{faces}}  \omega_f .
-\end{align*}
-
-One interesting thing to note is that both \( \vecbf{E}, \vecbf{F} \) can be precomputed without knowledge of the position of the satellite. 
-They are both solely functions of the vertices and edges of the polyhedral shape model.
-One a position vector \( \vecbf{r} \) is defined then the scalars \( \omega_f, L_e \) can be computed for each face and edge.
-
-Duplicate the equations for polyhedron model
-
-Give an outline of how to compute the potential (which equations and order)
-
-Cite the original werner papers
+One interesting thing to note is that both~\cref{eq:face_dyad,eq:edge_dyad} can be precomputed without knowledge of the position of the satellite. 
+They are both solely functions of the vertices and edges of the polyhedral shape model and are computed once and stored.
+Once a position vector \( \vecbf{r} \) is defined then the scalars~\cref{eq:edge_factor,eq:face_factor} can be computed for each face and edge.
+Finally,~\cref{eq:potential} is used to compute the gravitational potential on the spacecraft.
 
@@
 \end{align}
-where \( \vecbf{\Omega} \) is the instaneous angular velocity vector of the asteroid represented in the body-fixed frame, \( \vecbf{r} \) is the position of the particle in the body-fixed frame, and \( U_{\vecbf{r}} \) is the gradient of the gravitational potential~\cite{greenwood1988}.
+where \( \vecbf{\Omega} \) is the instaneous angular velocity vector of the asteroid represented in the body-fixed frame, \( \vecbf{r} \) is the position of the particle in the body-fixed frame, and \( U_{\vecbf{r}} \) is the gradient of the gravitational potential~\cite{scheeres2012a}.
 We assume that the asteroid rotates at a uniform rate, \( \norm{\vecbf{\Omega}} = \omega \), about the axis of the maximum moment of inertia, \( \vecbf{\Omega} = \omega \hat{\vecbf{z} }\).
@@
 	\begin{bmatrix} \dot{\vecbf{r}} \\ \dot{\vecbf{v}} \end{bmatrix} &=
+	\begin{bmatrix}\vecbf{v} \\ \vecbf{g} \parenth{\vecbf{r}} + \vecbf{h}\parenth{\vecbf{v}} + \vecbf{u} \end{bmatrix} ,
 \end{align}
-where the matrix \( G \) represents the
+where the terms \(\vecbf{g} \parenth{\vecbf{r}} \) and \( \vecbf{h}\parenth{\vecbf{v}} \) are given by
+\begin{align}\label{eq:state_space_terms}
+	\vecbf{g}\parenth{\vecbf{r}} = \begin{bmatrix}  U_x + \omega^2 x \\ U_y + \omega^2 y \\ U_z \end{bmatrix} ,\quad
+	\vecbf{h}\parenth{\vecbf{r}} = \begin{bmatrix} 2 \omega \dot{y} \\ -2 \omega \dot{x} \\ 0 \end{bmatrix} .
+\end{align}
 
-Cite scheeres and his book
+Since Castalia is a uniformly rotating asteroid, the equations of motion are time invariant when represented in the body-fixed frame.
+In addition, there exists an integral of motion, or a conserved quantity, the is constant for all motion of a particle, absent any other perturbing forces.
+The Jacobi constant, \( J (\vecbf{r} , \vecbf{v} ) \), is given by
+\begin{align}\label{eq:jacobi}
+	J \parenth{\vecbf{r}, \vecbf{v}} = \frac{1}{2} \omega^2 \parenth{x^2 + y^2} + U(\vecbf{r}) - \frac{1}{2} \parenth{\dot{x}^2 + \dot{y}^2 + \dot{z}^2} .
+\end{align}
+The Jacobi constant functions in a similar manner as used in three-body problem~\cite{szebehely1967}.
+\Cref{eq:jacobi} divides the phase space into distinct realms of possible motion.
+We can define zero-velocity surfaces using the Jacobi constant by fixing the value to a desired constant.
+The zero-velocity surfaces are the locus of points where the kinetic energy and hence velocity vanishes.
+
+Figure of zero velocity surfaces for each of the three planes
 
@@
 
-Define \Poincare section
+Define \Poincare section following the method of Scheeres
 
-\subsection{Optimal Control Formulation}
+4 dimensional \Poincare section so we need to discretize the direction using three angles
 

### 2016-08-06 manuscript.tex
Added some detail and plots to polyhedron section

@@
 As a result, only two faces meet at each edge while three faces meet at each vertex.
-Several asteroids have been accurately mapped from a combination of Earth based sensors as well as visiting spacecraft (CITE \href{http://sbn.psi.edu/pds/resource/rshape.html}{http://sbn.psi.edu/pds/resource/rshape.html}).
 Only the body-fixed vectors, and their associated topology, is required to define the exterior gravitational model.
-References~\citenum{werner1994} and~\citenum{werner1997} give a detailed derivation of the polyhedron model from first principles.
+References~\citenum{werner1994} and~\citenum{werner1997} give a detailed derivation of the polyhedron model.
 Here, we summarize the key developments and equations required for implementation and clarity.
 
-Insert picture of face and vectors
+{\LARGE Insert picture of face and vectors}
 
@@
 \end{align}
-where \( \vecbf{r}_e, \vecbf{r}_f \) is the vector from the spacecraft to any point on the respective edge or face.
+where \( \vecbf{r}_e, \vecbf{r}_f \) is the vector from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
 Furthermore we can use these definitions to define the attraction, gravity gradient matrix, and Laplacian are defined as
@@
 They are both solely functions of the vertices and edges of the polyhedral shape model and are computed once and stored.
-Once a position vector \( \vecbf{r} \) is defined then the scalars~\cref{eq:edge_factor,eq:face_factor} can be computed for each face and edge.
+Once a position vector \( \vecbf{r} \) is defined then the scalars given in~\cref{eq:edge_factor,eq:face_factor} can be computed for each face and edge.
 Finally,~\cref{eq:potential} is used to compute the gravitational potential on the spacecraft.
+
+In this work, we consider trajectories about asteroid 4769 Castalia.
+The shape model uses Doppler radar images to Castalia obstained at the Arecibo Observatory in 1989~\cite{hudson1994,neese2004}.
+We use the estimated rotation period of \SI{4.07}{\hour} with a nominal density of \SI{2.1}{\gram\per\centi\meter\cubed}~\cite{scheeres1996}.
+The shape model is composed of \num{4092} triangular faces and a rendering of the asteroid is provided in~\cref{fig:castalia_3d}.
+In addition, we also show a contour plot of the radius of Castlia in~\cref{fig:radius_contour}.
+\begin{figure}
+	\centering
+	\begin{subfigure}[htbp]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{castalia}
+		\caption{3D Shape Model of Castalia} \label{fig:castalia_3d}
+	\end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line)
+	\begin{subfigure}[htbp]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{radius_contour}
+		\caption{Radius contours of Castalia} \label{fig:radius_contour}
+	\end{subfigure} ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line)
+	\caption{Polyhedron Shape Model of 4769 Castalia}
+	\label{fig:castalia}
+\end{figure}
 
@@
 The Jacobi constant functions in a similar manner as used in three-body problem~\cite{szebehely1967}.
-\Cref{eq:jacobi} divides the phase space into distinct realms of possible motion.
 We can define zero-velocity surfaces using the Jacobi constant by fixing the value to a desired constant.
 The zero-velocity surfaces are the locus of points where the kinetic energy and hence velocity vanishes.
-
-Figure of zero velocity surfaces for each of the three planes
-
-Jacobi constant
-
-Zero velocity curves
-
-Equilibrium points. Cite work done with triaxial ellipsoids and other Castalia papers
-
-\subsection{Determining Periodic Orbits}
-
-Periodic orbit computation summary. Cite Scheeres 2000 (Evaluation of the Dynamic environment of an asteroid)
+Just as in the three-body problem, the Jacobi constant in~\cref{eq:jacobi} divides the phase space into distinct realms of possible motion.
+Similarly, there exist in general four equilibrium points and also their associated stable and unstable manifolds~\cite{scheeres1996,scheeres1994}.
+The properties of these manifolds play a critical role in the dynamics of trajecotries in their vicinity.
 
 \section{Reachability Set on \Poincare Section}
+
 Define reachability set
 
-Define \Poincare section following the method of Scheeres
+Define \Poincare section following the method of Scheeres.
+It is used in the periodic orbit determination~\cite{}
 

### 2016-08-07 manuscript.tex
Adding detail to reachability section

@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:introduction}
 
@@
 
-\section{Asteroid Model}
+\section{Asteroid Model}\label{sec:asteroid_model}
 
@@
 
-\subsection{Polyhedron Gravity Model}
+\subsection{Polyhedron Gravity Model}\label{sec:polyhedron_model}
 
@@
 
-\subsection{Spacecraft Equations of Motion}
+Mention that our model uses only 1024 faces for speed
+
+Show the plot of the equilibrium position as a function of the number of faces and show that it's where the knee in the curve exists
+
+\subsection{Spacecraft Equations of Motion}\label{sec:sc_eoms}
 
@@
 
-\section{Reachability Set on \Poincare Section}
+\section{Reachability Set on \Poincare Section}\label{sec:reachability}
 
+Typical optimal control methods, including both indirect and direct based methods, are highly dependent on an accurate initial guess.
+For indirect optimization, which is based on the calclus of variations, this results in the well-known two-point boundary value problem.
+Insight into the problem or insight by the designer is usually required to determine appropriate initial costates that will converge to the optimal solution and satisfy the desired constraints.
+To avoid this issue, we utilize the concept of the reachiblity set on a lower dimensional \Poincare section.
+By repeatedly constructing the reachability set we can achieve general transfers by determining set intersections on the \Poincare section.
+This alleviates the need to determine an accurate initial guess while offering some insight into the dynamics of neighboring trajectories
+
+The reachable set contains all possible trajectories that are achievable over a fixed time horizon from a defined initial condition, subject to the constraints of the system.
+Reachability theory has been applied to collision avoidance and safety planning in aerospace systems~\cite{holzinger2009,holzinger2011b}.
+The theory supporting reachabiilty analysis is directly derivable from optimal control theory~\cite{varaiya2000,lygeros2004}.
+Analytic, computation of reachability sets is only possible for a small class of potential systems.
+Here, we use numerical methods to solve an optimal control problem.
+The solution of this optimal control problem approximates a single solution that lies on the reachable set.
+\begin{figure}
+    \centering
+    \begin{scaletikzpicturetowidth}{0.5\textwidth}
+    \begin{tikzpicture}[scale=\tikzscale]
+        \coordinate [label=left:\textcolor{black}{\large \(\vec{x}_0\)}] (x0) at (-1,-2);
+        \coordinate [label=below:\textcolor{black}{\large  \(\vec{x}_n\)}] (xn) at (1,1);
+        \coordinate [label=left:\textcolor{black}{\large  \(\Sigma\)}] (sigma) at (-4,3);
+        %\coordinate [label=below:\textcolor{black}{\large  \(P(\vec{x})\)}] (P) at (0,-3.5);
+        % define the path of the flow with coordinates
+        \coordinate [label=right:\textcolor{black}{}] (f1) at (5,-2);
+        \coordinate [label=below:\textcolor{black}{\large  \(\phi(t,\vec{x}_0)\)}] (f2) at (2,-5);
+        \coordinate [label=right:\textcolor{black}{}] (f3) at (-4,-4);
+        \coordinate [label=right:\textcolor{black}{}] (f4) at (-4,-1);
+
+    %   \draw[help lines] (-10,-10) grid (10,10); %grid
+        \filldraw [black] (x0) circle [radius=3pt];
+        \filldraw [black] (xn) circle [radius=3pt];
+
+        \draw [ultra thick,black,->-](x0) to[out=20,in=90,distance=2cm] (f1) to[out=-90,in=0,distance=2cm] (f2) to[out=180,in=-45,distance=2cm] (f3) to[out=135,in=-135,distance=2cm] (f4) ;
+        \draw [ultra thick, black,dashed,->] (f4) to[out=45,in=180,distance=1cm] ($(xn)-(2,0)$);
+
+        \draw [ultra thick] plot [smooth cycle, tension=0.1, rotate=5] coordinates { (-4,-3) (4,-3) (4,3) (-4,3) };
+
+        \draw [thick,dashed] (xn) circle [radius=2cm]; % reachability set
+
+        \draw [thick,->] (xn) -- ($(xn) + (2.5,0)$);
+        \draw [thick,rotate=45,->] (xn) -- ($(xn) + (2.5,0)$);
+        \draw ($(xn) + (1,0)$) arc [start angle=0,end angle=45, radius=1];
+        \node [draw=none] at (2.4,1.5) {\Large \(\theta_d\)};
+        \draw [decorate,decoration={brace,amplitude=5pt},rotate=45] (xn) -- ($(xn) + (2,0)$);
+        \node [draw=none] at ($ (xn) + (0,1) $) {\Large \( J \)};
+    \end{tikzpicture}
+    \end{scaletikzpicturetowidth}
+    \caption{Reachability set on a \Poincare section\label{fig:reachability_set}}
+\end{figure}
+
+We seek to approximate the reachability set on a \Poincare section by solving an optimal control problem.
+The \Poincare section is chosen in a manner similar to the previous work in both the three-body problem as well analysis performed around asteroids to determine periodic orbits.
+Analysis in the three-body problem relies heaviliy on symmetries in the force fields.
+However, in our system model the gravitational potential, given by~\cref{eq:potential}, has no symmetries.
+In spite of this, it is still possible to determine periodic solutions through the application of a \Poincare map with surface of section chosen normal to surface in the phase space~\cite{scheeres2000}.
+For a periodic orbit, the trajectories will intersect the \Poincare section at two distinct points every half orbit.
+With the addition of a low thrust control input, we are able to expand the reachable set from a distinct point to a larger area on the \Poincare section.
+\Cref{fig:reachability_set} illustrates this methodology.
+Without any control input, the trajectories will intersect the \Poincare section at \( \vecbf{x}_n\).
+The addition of a control input allows the spacecraft to depart from the natural dynamics and intersect the section at another location.
+We use the cost function \( J \) to define a distance metric on the \Poincare section.
+Maximization of \( J \), or the minimization of \( -J \), along various directions on the \Poincare section allows us to generate the larges reachability set under the bounded control input.
+
+We define the \Poincare section as the surface normal to \( y = 0 \).
+Following convention, the \Poincare map is defined as the map from one transversal crossing of the surface \( y = 0\) to the next.
+Using the method of Reference~\cite{scheeres2000}, we are able to remove \( y \) and \( \dot{y} \), creating a four-dimensional map.
+The \Poincare section, \( \Sigma \) then becomes
+\begin{align}\label{eq:poincare_section}
+    \Sigma = \braces{\parenth{x, \dot{x}, z, \dot{z}} | y(t_f) = 0 }.
+\end{align}
+We use this section to compute periodic orbits that serve as the initial and target of our transfer.
+In addition, this section serves as a lower dimensional space upon which we approximate the reachability set.
+
+An optimal control problem is defined by the cost function
+\begin{align}\label{eq:cost}
+    J = -\frac{1}{2} \left( \vecbf{x}(t_f) - \vecbf{x}_{n}(t_f)\right)^T 
+    \begin{bmatrix}
+        1 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 1 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 1 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 0 & 0 & 1 \\
+    \end{bmatrix}
+    \left( \vecbf{x}(t_f) - \vecbf{x}_{n}(t_f)\right) ,
+\end{align}
+where \( \vecbf{x}_n(t_f) \) is the final state of a control-free trajectory, while the term \( \vecbf{x}(t_f)\) is the final state of a trajectory under the influence of the control input.
+Maximization of the distance between \( \vecbf{x}_n \) and \(\vecbf{x} \), on the \Poincare section defined in~\cref{eq:poincare_section}, is equivalent to the minimization of \( J \) defined in~\cref{eq:cost}.
+We ensure that the trajectories 
 Define reachability set
@@
 Define \Poincare section following the method of Scheeres.
-It is used in the periodic orbit determination~\cite{}
+It is used in the periodic orbit determination.
 
@@
 
-\section{Numerical Simulation}
+\section{Numerical Simulation}\label{sec:simulation}
 
@@
 
-\section{Conclusion}
+\section{Conclusions}\label{sec:conclusions}
 

### 2016-08-07 manuscript.tex
Starting on optimal control problem

@@
 Maximization of the distance between \( \vecbf{x}_n \) and \(\vecbf{x} \), on the \Poincare section defined in~\cref{eq:poincare_section}, is equivalent to the minimization of \( J \) defined in~\cref{eq:cost}.
-We ensure that the trajectories 
-Define reachability set
+We ensure that the trajectories intersect the \Poincare section through the use of terminal constraints.
+In addition, we use the terminal constraints to define a specific direction along which we seek to minimize the cost~\cref{eq:cost}.
+Since the \Poincare section is four-dimensional we parameterize a direction in \( \R^4 \)  using three angles \( \phi_1, \phi_2 , \phi_3 \) to define the terminal constraints
+\begin{align}\label{eq:terminal_constraints}
+    \begin{split}
+        m_1 &= y = 0 \\
+        m_2 &= \parenth{\sin \phi_{1_{d}}} \parenth{ x_1^2 + x_2^2 + x_3^2 + x_4^2} - x_1^2 = 0, \\
+        m_3 &= \parenth{\sin \phi_{2_{d}}} \parenth{ x_2^2 + x_3^2 + x_4^2} - x_2^2 = 0, \\
+        m_4 &= \parenth{\sin \phi_{3_{d}}} \parenth{ 2 x_3^2 + 2 x_3 \sqrt{x_4^2 + 2 x_4^2}} - x_3 - \sqrt{x_4^2 + x_3^2} = 0. 
+    \end{split}
+\end{align}
+We make use of the difference states \( \parenth{x_1, x_2 ,x_3, x_4 }\) which are defined as
+\begin{align}\label{eq:diff_states}
+    \begin{split}
+        x_1 &= x(t_f) - x_n(t_f) , \\
+        x_2 &= z(t_f) - z_n(t_f) , \\
+        x_3 &= \dot{x}(t_f) - \dot{x}_n(t_f) , \\
+        x_4 &= \dot{z}(t_f) - \dot{z}_n(t_f) . \\
+    \end{split}
+\end{align}
+The constraint \( m_1 = 0 \) ensures that the terminal states lies on the \Poincare section.
+The constraints \( m_2, m_3, m_4 \) are used to define a direction on the \Poincare section.
+Finally, we also incorporate a control thrust magnitude constraint given by
+\begin{align}\label{eq:control_constraint}
+    \vecbf{u}^T \vecbf{u} - u_m^2 \leq 0 ,
+\end{align}
+where \( u_m \) is the maximum thrust magnitude.
+This constraint assumes that the control thrust may be orientated in any direction yet the thrust is variable but limited.
+The goal is to determine the control history \( \vecbf{u}(t) \) such that teh cost function~\cref{eq:cost} is minimized while subject to the equations of motion~\cref{eq:body_eoms} and the constraints~\cref{eq:control_constraint,eq:terminal_constraints}.
 
-Define \Poincare section following the method of Scheeres.
-It is used in the periodic orbit determination.
-
-4 dimensional \Poincare section so we need to discretize the direction using three angles
-
-Formulate OCP to generate the reachability set
-
-Discuss the constraints and angles on the four dimensional space of the section
+% How do you solve the optimal control problem
 

### 2016-08-08 manuscript.tex
Added more detail to reachability section

@@
 \begin{align}\label{eq:control_constraint}
-    \vecbf{u}^T \vecbf{u} - u_m^2 \leq 0 ,
+    c(\vecbf{u}) = \vecbf{u}^T \vecbf{u} - u_m^2 \leq 0 ,
 \end{align}
@@
 % How do you solve the optimal control problem
+We apply a standard calculus of variations approach to solve our optimal control problem~\cite{bryson2002}.
+Using the Euler-Lagrange equations we arrive at the necessary conditions for optimality
+\begin{align}\label{eq:necc_conditions}
+    \begin{split}
+        \dot{\vecbf{x}} ^T &= \deriv{H}{\vecbf{\lambda}} ,\\
+        \dot{\vecbf{\lambda}}^T &= \deriv{H}{\vecbf{x}} , \\
+        0 &= \deriv{\phi}{x}^T + \deriv{\vecbf{m}}{x}^T \vecbf{\beta} - \vecbf{\lambda}^T(t_f) , \\
+        0 &= \deriv{H}{\vecbf{u}} + \mu^T \deriv{c}{\vecbf{u}} ,
+    \end{split}
+\end{align}
+where the Hamiltonian, \( H\), is defined as
+\begin{align}\label{eq:hamiltonian}
+    H = \vecbf{\lambda}_r^T \vecbf{v} + \vecbf{\lambda}_v^T \parenth{\vecbf{g}(\vecbf{r}) + \vecbf{h}(\vecbf{v}) + \vecbf{u}}.
+\end{align}
+The costate is given by \( \vecbf{\lambda} = \begin{bmatrix} \vecbf{\lambda}_r & \vecbf{\lambda}_v \end{bmatrix}^T \in \R^{6 \times 1}\), \( \vecbf{\beta} \in \R^{4 \times 1} \) are the additional Lagrange multiplers associated with the terminal constraints in~\cref{eq:terminal_constraints}, and \( \mu \) is a Lagrange multipler associated with the control constraint in~\cref{eq:control_constraint}.
+
+We can redefine the optimal control in terms of the costate by rewritting the necessary condition as
+\begin{align*}
+    \vecbf{u} = - \frac{u_m^2}{2 \mu} \vecbf{\lambda}_v .
+\end{align*}
+We use this along with the control constraint to solve for the Lagrange multipler \( \mu \)
+\begin{align*}
+    \mu = \pm \frac{u_m}{2} \norm{\vecbf{\lambda}_v} .
+\end{align*}
+Finally, we use the second-order necessary condition to determine the correct sign of \( \mu \) and find the optimal control input for the reachable set as
+\begin{align}\label{eq:optimal_control}
+    \vecbf{u} = - u_m \frac{\vecbf{\lambda}}{\norm{\vecbf{\lambda}}} .
+\end{align}
+
+This optimal control formulation results in a two point boundary value problem.
+We use a shooting method to determine the initial costates, \( \vecbf{\lambda}(t_0)\), such that the terminal constraints are satisfied.
+In addition, we implement a multiple shooting method which sub-divides the the entire trajectory into small sub-intervals~\cite{stoer2013}.
+We incorporate additional interior constraints to ensure a continuous trajectory at the patch points between the sub-intervals.
+The multiple shooting method reduces the sensitivity of the terminal states to the initial conditions and alleviates many of the issues of single shooting approaches.
 

### 2016-08-08 manuscript.tex
Started on results section

@@
 
+We present an example transfer of a spacecraft about the asteroid 4769 Castalia. 
+Our equations of motion, given by~\cref{eq:eoms}, are an idealized version of the dynamics of a spacecraft.
+For example, the model does not include the effect of mass transfer from propellant usage. 
+We instead model the control input as a generic acceleration vector in the body-fixed asteroid frame. 
+The thrust magnitude constraint in~\cref{eq:control_constraint} is chosen to emulate a physically realizable thruster system.
+In this analysis, we assume \( u_m = \SI{0.1}{\milli\meter\per\second\squared}\) which is equivalent to a thrust of approximately \SI{100}{\milli\newton} for a \SI{1000}{\kilo\gram} spacecraft.
+This amount of thrust is typical of many current ion or hall effect thrusters and is in operation in several current missions (cite Goebels Fundamentals of electric propulsion and Dawn thruster paper by choueiri2009new).
+
+The objective is to transfer the spacecraft between two periodic equatorial orbits about Castalia.
+The initial and target orbits are periodic solutions about Castlia computed using the method introduced by Reference~\citenum{scheeres2003}.
+The initial conditions for both orbits are defined in the body-fixed frame as
+\begin{align}\label{sec:initial_transfer}
+    \vecbf{x}_i = 
+    \begin{bmatrix}
+        1.4973 \\ 0 \\ 0.0061 \\ 0\\ -0.0009 \\ 0
+    \end{bmatrix} ,
+    \quad
+    \vecbf{x}_t =
+    \begin{bmatrix}
+        2.9786 \\ 0 \\ 0.0012 \\ 0\\ -0.0011 \\ 0
+    \end{bmatrix} .
+\end{align}
+\Cref{fig:initial_transfer} shows the initial and desired periodic orbits which lie in the equatorial plane of Castalia.
+Our goal is to transfer from a lower altitude to a higher altitude while remaining in the equatorial plane of the asteroid.
+This type of scenario would occur frequently during mapping and observation missions to asteroids.
+\begin{figure}[htbp]
+    \centering 
+    \begin{subfigure}[htbp]{0.5\textwidth} 
+        \includegraphics[width=\textwidth]{initial_transfer} 
+        \caption{Equatorial View} \label{fig:eq_initial_transfer} 
+    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \begin{subfigure}[htbp]{0.5\textwidth} 
+        \includegraphics[width=\textwidth]{initial_transfer_3d} 
+        \caption{3D view} \label{fig:initial_transfer_3d} 
+    \end{subfigure} ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \caption{Initial and target periodic orbits}
+    \label{fig:initial_transfer} 
+\end{figure}
+In this transfer example we also have used a reduced model of Castalia.
+Rather than using the full \num{4092} face model we reduce the number of faces to \num{1024}. 
+This greatly speeds up the computation with only a small difference in the potential field or shape model.
+
+We first compute the reachability set originating from the initial periodic orbit at \( \vecbf{x}_i\) for a fixed time of flight and bounded control magnitude as defined preivously.
+Since the target periodic orbit also lies in the equatorial plane, we augment~\cref{eq:terminal_constraints} with an additional constraint \( m_5 = z = 0\) to ensure that the trajectories remain in the equatorial plane.
+The reachability set is computed by solving the two-point boundary value problem using a multiple shooting algorithm to satisfy the necessary conditions in~\cref{eq:necc_conditions}.
+The reachability set is generated on the lower dimensional \Poincare section and is composed of the terminal states in the \( \parenth{x,z,\dot{x},\dot{z} } \) space.
+We visualize the section using the two figures in~\cref{fig:poincare_section}.
+\begin{figure}[htbp]
+    \centering 
+    \begin{subfigure}[htbp]{0.5\textwidth} 
+        \includegraphics[width=\textwidth]{figures/poincare_xvsxdot.pdf} 
+        \caption{\( x \) vs. \( \dot{x} \) \Poincare section} \label{fig:poincare_xvsxdot} 
+    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \begin{subfigure}[htbp]{0.5\textwidth} 
+        \includegraphics[width=\textwidth]{figures/poincare_zvszdot.pdf} 
+        \caption{\( z \) vs. \( \dot{z} \) \Poincare section} \label{fig:poincare_zvszdot} 
+    \end{subfigure}
+    \caption{\Poincare section visualization}
+    \label{fig:poincare_section} 
+\end{figure}
+These two-dimensional sections allow us to visualize the four-dimensional \Poincare section of~\cref{eq:poincare_section}.
+
+we use a lower number of faces to speed up the computation
+
+Transfer is between equatorial periodic orbits in the body fixed frame
+
+We compute the reachability set given a fixed initial state over a fixed time span
+
+We then determine the state(which is on the reachability set) which minimizes the distance to the target
+
+This state is used to intialize the next stage
+
+Repeat this until we can achieve both position coordinates on the various \Poincare sections
+
+The velocities do not match but a simple optimal control scheme is used to arrive at the target
+
 Transfer about asteroid Castalia - cite some Scheeres papers
@@
 
-Thruster magnitude is chosen to emulate some real thrusters - cite the Dawn paper
-
 \section{Conclusions}\label{sec:conclusions}
 
-\section*{Acknowledgments}
+\section*{Acknowledgments}\label{sec:aknowledgments}
 

### 2016-08-09 manuscript.tex
Almost done with results section

@@
 The constraints \( m_2, m_3, m_4 \) are used to define a direction on the \Poincare section.
+We approximate the entire reachable set by discretizing the space of angles \(\phi_1, \phi_2, \phi_3 \).
+By convention we assume that the angles lie in the following range
+\begin{align*}
+    \phi_1, \phi_2 &\in [ 0, \pi ) ,\\
+    \phi_3 &\in [ 0 , 2 \pi ) ,
+\end{align*}
+such that we parameterize all directions on the three sphere, \(\S^3\).
 Finally, we also incorporate a control thrust magnitude constraint given by
@@
 The reachability set is generated on the lower dimensional \Poincare section and is composed of the terminal states in the \( \parenth{x,z,\dot{x},\dot{z} } \) space.
+We approximate the reachability set by discritizing each of the angles \( \phi_1, \phi_2 , \phi_3 \) into ten discrete steps. 
+This results in a total of \(10^3\) trajectories which approximate the reachability set on the \Poincare section.
 We visualize the section using the two figures in~\cref{fig:poincare_section}.
@@
 \end{figure}
-These two-dimensional sections allow us to visualize the four-dimensional \Poincare section of~\cref{eq:poincare_section}.
+These two-dimensional sections allow us to visualize the four-dimensional \Poincare section defined by~\cref{eq:poincare_section}.
+The first stage of the transfer is represented by the magenta markers in~\cref{fig:poincare_section}.
+From~\cref{fig:poincare_xvsxdot}, we can see that the reachablity set has grown in the \( \dot{x} \) dimension but has not been enlarged much in the \( x \) direction.
+Similarily,~\cref{fig:poincare_zvszdot} shows an increase in the \( \dot{z} \) component while still maintaining the \( z = 0 \) terminal constraint.
+From the reachability set, we chose a trajectory and terminal state which minimizes a distance metric \( d(\vecbf{x}_f,\vecbf{x}_t) \) to the desired target
+\begin{align}\label{eq:reach_dist}
+    d = \sqrt{k_x \parenth{x_f - x_t }^2 + k_z \parenth{z_f - z_t }^2 + k_{\dot{x}}\parenth{\dot{x}_f - \dot{x}_t }^2 + k_{\dot{z}}\parenth{\dot{z}_f - \dot{z}_t }^2} ,
+\end{align}
+where \( k_x, k_z, k_{\dot{x}}, k_{\dot{z}} \) are used to weight the relative importance of each of the components of the \Poincare section.
+\Cref{fig:phi_distance} shows the distance to the target for the chosen discretization of \( \phi_i \).
+\begin{figure}[htbp] 
+    \centering 
+    \begin{subfigure}[htbp]{0.3\textwidth} 
+        \includegraphics[width=\textwidth]{figures/phi1.pdf} 
+        \caption{ \( \phi_1 \)} \label{fig:phi1} 
+    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \begin{subfigure}[htbp]{0.3\textwidth} 
+        \includegraphics[width=\textwidth]{figures/phi2.pdf} 
+        \caption{\( \phi_2 \)} \label{fig:phi2} 
+    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \begin{subfigure}[htbp]{0.3\textwidth} 
+        \includegraphics[width=\textwidth]{figures/phi3.pdf} 
+        \caption{\( \phi_3 \)} \label{fig:phi3} 
+    \end{subfigure} 
+    \caption{Variation of \(d(\vecbf{x}_f,\vecbf{x}_t)\) due to varying \( \phi_i\)}
+    \label{fig:phi_distance} 
+\end{figure}
 
-we use a lower number of faces to speed up the computation
+The trajectory which minimizes \( d \) is indicated by the red marker in~\cref{fig:poincare_section ,fig:phi_distance}.
+Since the reachability set does not include the target we use the minimum state from the first stage to initialize another reachability computation.
+Once again we compute the reachability set by discritizing the space on the \Poincare section using the angles \( \phi_i \).
+This second stage, represented by the green markers in~\cref{fig:poincare_section,fig:phi_distance}, further increase the \( x \) component but does not reach the target orbit.
+As a result, a third stage is generated in a similar manner and shown by the green markers in~\cref{fig:poincare_section ,fig:phi_distance}.
+We can see in~\cref{fig:poincare_section} that the reachability set of the third stage includes both the \( x \) and \( z\) of the target periodic orbit.
+At the same time there is a relatively large difference between the \( \dot{x} \) and \( \dot{z} \) components of the third stage and the target orbit.
+In practice this is not a large concern as we have direct control over the spacecraft velocity via the control input.
 
-Transfer is between equatorial periodic orbits in the body fixed frame
+With the reachability set encompassing the target orbit, we can generate a final transfer to the target.
+We use the minimum state calculated from the final stage to serve as the initial condition of the transfer.
+A final optimal transfer is computed to satisfy the fixed terminal state \( \vecbf{x}(t_f) = \vecbf{x}_t \) and the bounded control magnitude constraint.
+\Cref{fig:trajectory} shows the entire transfer trajectory, from the three reachable set trajectories as well as the final transfer to the target.
+\begin{figure}[htbp] 
+    \centering 
+    \begin{subfigure}[htbp]{0.5\textwidth} 
+        \includegraphics[width=\textwidth]{figures/trajectory.pdf} 
+        \caption{Equatorial view of transfer} \label{fig:trajectory_up} 
+    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \begin{subfigure}[htbp]{0.5\textwidth} 
+        \includegraphics[width=\textwidth]{figures/trajectory_3d.pdf} 
+        \caption{Out of plane view} \label{fig:trajectory_3d} 
+    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \caption{Complete transfer trajectory}
+    \label{fig:trajectory} 
+\end{figure}
 
-We compute the reachability set given a fixed initial state over a fixed time span
+The transfers show a large out of plane movement for a planar transfer
 
-We then determine the state(which is on the reachability set) which minimizes the distance to the target
+Show a plot of the control input
 
-This state is used to intialize the next stage
-
-Repeat this until we can achieve both position coordinates on the various \Poincare sections
-
-The velocities do not match but a simple optimal control scheme is used to arrive at the target
-
-Transfer about asteroid Castalia - cite some Scheeres papers
-
-Plots of \Poincare section
-
-Full trajectory plots
+Mention somewhere up above that we're trying to determine a reachability set on a \Poincare section
 

### 2016-08-09 manuscript.tex
First draft of paper. Need to proofreead

@@
   {\normalsize\itshape
-   Mechanical and Aerospace Engineering, George Washington University, 800 22nd St NW, Washington DC }\\
+   George Washington University, Washington, District of Columbia }\\
    }
@@
 
-\begin{abstract}
-Write an awesome abstract
+\begin{abstract}\label{sec:abstract}
 
-Use the reachability set to compute transfers
+We present a computational approach for the design of continuous low thrust transfers around asteroids.
+These transfers are computed through the use of a reachability set which is generated on a lower dimensional \Poincare surface.
+Computation of the reachable set alleviates the need to generate an accurate initial guess for optimization.
+Successive computation of the reachable set allows for the design of general transfer trajectories.
+We demonstrate this method by determining a transfer trajectory about the asteroid 4769 Castalia.
 
-extend work already done in three body problem to motion around asteroid
-
-Numerical example for asteroid 4769 Castalia
 \end{abstract}
-
-\section*{Nomenclature}
-
-\begin{tabbing}
-  XXX \= \kill% this line sets tab stop and adds a newline
-  $J$ \> Jacobian Matrix \\
-  $f$ \> Residual value vector \\
-  $x$ \> Variable value vector \\
-  $F$ \> Force, \si{\newton} \\
-  $m$ \> Mass, \si{\kilo\gram} \\
-  $\Delta x$ \> Variable displacement vector \\
-  $\alpha$ \> Acceleration, \si{\meter\per\second\squared} \\[5pt]
-  \textit{Subscript}\\
-  $i$ \> Variable number \\
-\end{tabbing}
 
@@
 
-\subsection{Shape Model}
-Cite location of shape model database
+In this analysis we consider transfers about the asteroid 4769 Castalia.
+Castalia has an accurate shape model and it is also considered a potentially hazardous asteroid with a possibility of Earth impact~\cite{hudson1994}.
+We also model the graviational potential field of Castalia using a polyhedron gravity model instead of using a spherical harmonic expansion.
+The spherical harmonic expansion is a popular method of representing the gravity field~\cite{scheeres1996}.
+Approximations are possible by truncating the infinite order series to fixed set of coefficients, with the most important terms corresponding to the second order and degree~\cite{scheeres1994}.
+The approximation error is generally small given a sufficient amount of terms. 
+However, when evaluated close to the body the series expansion will diverge and is no longer accurate.
 
-Cite Scheeres orbits close to 4769 Castalia
-
-Assuming constant rotation rate for asteroid
-
-Mention we're looking at asteroid 4769 Castalia
+In contrast, the polyhedron model results in an exact closed form expression of the gravitational potential field~\cite{werner1994}.
+In addition, the model results in the exact potential for the given shape
+However, the calculation of the potential, or the acceleration, requires a summation over every face of the polyhedron. 
+As a result, it typically requires a large amount of computation in contrast to the harmonic expansion. 
+However, the formulation is well suited to parallelization and improvements with efficient coding practices. 
+Finally, the polyhedron method is well suited to trajectories passing close to the body and offers a simple metric to determine if a particle is inside the asteroid.
 
@@
 References~\citenum{werner1994} and~\citenum{werner1997} give a detailed derivation of the polyhedron model.
-Here, we summarize the key developments and equations required for implementation and clarity.
-
-{\LARGE Insert picture of face and vectors}
+Here, we summarize the key developments and equations required for implementation.
 
@@
     \centering
-    \begin{subfigure}[htbp]{0.5\textwidth}
+    \begin{subfigure}[htbp]{0.45\textwidth}
         \includegraphics[width=\textwidth]{castalia}
@@
     \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[htbp]{0.5\textwidth}
+    \begin{subfigure}[htbp]{0.45\textwidth}
         \includegraphics[width=\textwidth]{radius_contour}
@@
     \centering
-    \begin{scaletikzpicturetowidth}{0.5\textwidth}
+    \begin{scaletikzpicturetowidth}{0.3\textwidth}
     \begin{tikzpicture}[scale=\tikzscale]
@@
 Following convention, the \Poincare map is defined as the map from one transversal crossing of the surface \( y = 0\) to the next.
-Using the method of Reference~\cite{scheeres2000}, we are able to remove \( y \) and \( \dot{y} \), creating a four-dimensional map.
+Using the method of Reference~\citenum{scheeres2000}, we are able to remove \( y \) and \( \dot{y} \), creating a four-dimensional map.
 The \Poincare section, \( \Sigma \) then becomes
@@
     \centering 
-    \begin{subfigure}[htbp]{0.5\textwidth} 
+    \begin{subfigure}[htbp]{0.45\textwidth} 
         \includegraphics[width=\textwidth]{initial_transfer} 
@@
     \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
-    \begin{subfigure}[htbp]{0.5\textwidth} 
+    \begin{subfigure}[htbp]{0.45\textwidth} 
         \includegraphics[width=\textwidth]{initial_transfer_3d} 
@@
     \centering 
-    \begin{subfigure}[htbp]{0.5\textwidth} 
+    \begin{subfigure}[htbp]{0.45\textwidth} 
         \includegraphics[width=\textwidth]{figures/poincare_xvsxdot.pdf} 
@@
     \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
-    \begin{subfigure}[htbp]{0.5\textwidth} 
+    \begin{subfigure}[htbp]{0.45\textwidth} 
         \includegraphics[width=\textwidth]{figures/poincare_zvszdot.pdf} 
@@
     \end{subfigure} 
-    \caption{Variation of \(d(\vecbf{x}_f,\vecbf{x}_t)\) due to varying \( \phi_i\)}
+    \caption{Variation of \(d(\vecbf{x}_f,\vecbf{x}_t)\) due to \( \phi_i\)}
     \label{fig:phi_distance} 
@@
     \centering 
-    \begin{subfigure}[htbp]{0.5\textwidth} 
+    \begin{subfigure}[htbp]{0.45\textwidth} 
         \includegraphics[width=\textwidth]{figures/trajectory.pdf} 
@@
     \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
-    \begin{subfigure}[htbp]{0.5\textwidth} 
+    \begin{subfigure}[htbp]{0.45\textwidth} 
         \includegraphics[width=\textwidth]{figures/trajectory_3d.pdf} 
@@
 \end{figure}
-
+It is interesting to note the while both the initial and target periodic orbit lie in the equatorial plane, the reachablity trajectories show a relatively large out of plane component during the transfers.
+In spite of this out of plane movement, the reachability set approaches and meets the target orbit. 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/control.pdf}
+    \caption{Control history \label{fig:control}}
+\end{figure}
+\Cref{fig:control} shows the control input required during the manuever.
 The transfers show a large out of plane movement for a planar transfer
-
-Show a plot of the control input
-
-Mention somewhere up above that we're trying to determine a reachability set on a \Poincare section
+We can see that the control constraint in~\cref{eq:control_constraint} is satisfied over the entire trajectory.
 
@@
 
-\section*{Acknowledgments}\label{sec:aknowledgments}
-
-A place to recognize others.
+In this paper, an optimal transfer process, which combines the concepts of reachability and \Poincare section, is used to generate a transfer between periodic orbits about the asteroid 4769 Castalia.
+We have linked several computations of the reachability set on a \Poincare section in order to design a transfer trajectory.
+The use of the \Poincare section allows for trajectory design on a lower dimensional space and is an extension of its well-known use in the analysis of periodic orbits.
+We use an indirect optimal control formulation to incorporate a control magnitude contraint and several terminal state constraints.
+Utilizing the reachability set alleviates the need to determine accurate initial conditions that allow for convergence of the optimal solution.
+In addition, the use of the polyhedron gravitational model gives simple method of extending this work to any small body that also posseses a defined shape model.
 

### 2016-08-09 manuscript.tex
Working on proofreading and correcting errors

@@
 We present a computational approach for the design of continuous low thrust transfers around asteroids.
-These transfers are computed through the use of a reachability set which is generated on a lower dimensional \Poincare surface.
+These transfers are computed through the use of a reachability set generated on a lower dimensional \Poincare surface.
 Computation of the reachable set alleviates the need to generate an accurate initial guess for optimization.
@@
 These small bodies offer great insight into the early formation of the solar system.
-This insight offers additional detail into the formation of the Earth and also the probable formation of other planetary systems.
+This insight offers additional detail into the formation of the Earth and also the probable formation of other planetary bodies.
 Of particular interest are those near-Earth asteroids (NEA) which inhabit heliocentric orbits in vicinity of the Earth.
@@
 Asteroids and comets are the greatest threat to future civilizations and as a result there is a focused effort to mitigate these risks.
-In spite of the great interest in asteroids, the operation of spacecraft in thier vicinity is a challenging problem.
+In spite of the great interest in asteroids, the operation of spacecraft in their vicinity is a challenging problem.
 
@@
 While there has been significant study of interplanetary transfer trajectories, relatively less analysis has been conducted on operations in the vicinity of asteroids.
-The dynamic environment of around asteroids is strongly perturbed and challenging for analysis and mission operation.
-Due to their small size and therefore low gravitational attraction asteroids have irregular shapes and potentially chaotic spin states.
-Furthermore, due to the low gravitational attraction, other non-gravitional effects, such as solar radiation pressure, become more significant.
-The orbital enviornment is in general quite complex and analytical insights are difficult to generate.
+The dynamic environment around asteroids is strongly perturbed and challenging for analysis and mission operation.
+Due to their small size, resulting in a low gravitational attraction, asteroids have irregular shapes or potentially chaotic spin states.
+Furthermore, due to their low mass other non-gravitational effects, such as solar radiation pressure or third-body effects, become much more significant.
+As a result, the orbital environment is in general quite complex and it is difficult to generate analytical insights.
 
@@
 % most use a spherical harmonic model or a ellipsoid model but we use a polyhedron model
-An accurate gravitional potential model is neccessary for the operation of spacecraft about asteroids.
+An accurate gravitational potential model is necessary for the operation of spacecraft about asteroids.
 Additionally, a detailed shape model of the asteroid is needed for trajectories passing close to the body.
@@
 Radio tracking data of an orbiting spacecraft allows one to estimate the series coefficients.
-The harmonic representation are guaranteed to converge outside of the circumscribing sphere and can be truncated at a finite order based on accuracy requirements.
+The harmonic representation is guaranteed to converge outside of the circumscribing sphere and can be truncated at a finite order based on accuracy requirements.
 However, the harmonic expansion is always an approximation as a result of the infinite order series used in the representation.
@@
 As a result, additional steps must be taken to determine a valid harmonic expansion for particles close to the body.
-This results in a cumbersome gravity field model that requires additional constraints to ensure continuity and validity at the radius of the circumscribing sphere~\cite{werner1996}.
+This results in a cumbersome gravity field model that requires additional constraints to ensure continuity and validity at the radius of the circumscribing sphere~\cite{werner1994 ,werner1996}.
 Instead, we model the asteroid as a constant-density polyhedron and avoid the issues of the harmonic expansion while enabling several other useful advantages.
 
-% benefits of the polyhedron model
-A polyhedral model of the surface of an asteroid can be determined from remote optical or radar sensors.
-The faces of the polyhedron can be large or small and allows for fine detail such as depression, craters, ridges, or interior voids.
-In addition, there is no requirement for the body to be modeled at a uniformly high resolution so small details can be incorprated with minimal cost.
-From the shape model, an analytical, closed form expression for the gravitational potential can be derived.
-The polyhedral approach provides an accurate gravitational model consistent with the resolution of the shape and the chosen discretization.
-Furthermore, the polyhedron model is an exact solution up to the surface of the body.
-Therefore, this model is ideal for missions traversing large region both close and far from the asteroid.
-
-% similarity to the three body problem
-The irregular shape of asteroids leads to a richer dynamics as compard to the familar Kepler's problem, which is based on a point mass assumption.
-The motion of particles around asteroids is modeled using the restricted full two-body problem.
-This model has many similarities with the restricted three body problem, and much of the theory developed there is also applicable.
-There has been much work in characterizing the relative equilibria and periodic orbits in the three-body problem.
-In addition, orbital transfers have been designed which exploit the invariant manifolds of the three-body problem for low-energy manuevers~\cite{mingotti2011,grebow2011}.
-The similarity of the three-body problem to motion around astreroids allows for much of the same theory to be applied to the asteroid problem.
-More recently, the invariant manifolds around asteroids have been proposed for orbital transfers and landing manuevers~\cite{mondelo2010,herrera2014}.
-
 % use of low thrust propulsion
-
 The application of optimal control methods for orbital trajectory design is nontrivial.
@@
 
-% SYSTEMATIC DESIGN TO AVOID DIFFICULTIES IN CHOOSING A GOOD INITIAL GUESS
-% CAPTURE LONG TERM EFFECTS OF LOW THRUST ACCURATELY IN NUMERICAL SIMULATION
+% similarity to the three body problem
+The irregular shape of asteroids leads to a richer dynamics as compared to the familiar Kepler's problem.
+The motion of particles around asteroids is modeled using the restricted full two-body problem.
+This model has many similarities with the restricted three body problem, and much of the theory developed in the three-body problem is also applicable.
+The similarity of the three-body problem to motion around asteroids allows for much of the same theory to be applied to the asteroid problem~\cite{mondelo2010,herrera2014}.
 In this paper, we extend the design method developed in the three-body problem to motion about asteroids~\cite{kulumani2015}.
@@
 Given an initial condition and fixed time horizon, the reachable set is the set of states attainable, subject to the operational constraints of the spacecraft.
+We calculate the reachable set on a lower dimensional \Poincare section which allows a 
 In addition, the generation of the reachable set allows for a more systematic method of determining initial conditions and eases the burden on the designer.
@@
 In this analysis we consider transfers about the asteroid 4769 Castalia.
-Castalia has an accurate shape model and it is also considered a potentially hazardous asteroid with a possibility of Earth impact~\cite{hudson1994}.
-We also model the graviational potential field of Castalia using a polyhedron gravity model instead of using a spherical harmonic expansion.
+Castalia has an accurate shape model and is also considered a potentially hazardous asteroid with a possibility of Earth impact~\cite{hudson1994}.
+We model the gravitational potential field of Castalia using a polyhedron gravity model instead of using a spherical harmonic expansion.
 The spherical harmonic expansion is a popular method of representing the gravity field~\cite{scheeres1996}.
@@
 Finally, the polyhedron method is well suited to trajectories passing close to the body and offers a simple metric to determine if a particle is inside the asteroid.
+
+% benefits of the polyhedron model
+A polyhedral model of the surface of an asteroid can be determined from remote optical or radar sensors.
+The faces of the polyhedron can be large or small and allows for fine detail such as depression, craters, ridges, or interior voids.
+In addition, there is no requirement for the body to be modeled at a uniformly high resolution so small details can be incorporated with minimal cost.
+From the shape model, an analytical, closed form expression for the gravitational potential can be derived.
+The polyhedral approach provides an accurate gravitational model consistent with the resolution of the shape and the chosen discretization.
+Furthermore, the polyhedron model is an exact solution up to the surface of the body.
+Therefore, this model is ideal for missions traversing large regions both close and far from the asteroid.
 
@@
 \end{align}
-Each edge is a member of two faces and has an outward pointing edge normal vector, given in~\cref{eq:edge_normal}, perpindicular to both the edge and the face normal.
-For the edge connecting the vectors \( \vecbf{v}_1 \) and \( \vecbf{v}_2 \) which are shared between the faces \(A\) and \( B\) the per edge dyad is given by
+Each edge is a member of two faces and has an outward pointing edge normal vector, given in~\cref{eq:edge_normal}, perpendicular to both the edge and the face normal.
+For the edge connecting the vectors \( \vecbf{v}_1 \) and \( \vecbf{v}_2 \) which are shared between the faces \(A\) and \( B\), the per edge dyad is given by
 \begin{align}\label{eq:edge_dyad}
@@
 \end{align}
-The edge dyad \( \vecbf{E}_e \) is defined for each edge and a function of the two adjacent faces meeting at the edge.
-The face dyad \( \vecbf{F}_f \) is defined for each face and is a function of the face normal vector.
+The edge dyad, \( \vecbf{E}_e \), is defined for each edge and a function of the two adjacent faces meeting at the edge.
+The face dyad, \( \vecbf{F}_f \), is defined for each face and is a function of the face normal vector.
 
@@
 Finally,~\cref{eq:potential} is used to compute the gravitational potential on the spacecraft.
+The Laplacian, defined in~\cref{eq:laplacian}, gives a simple method to determine if the spacecraft has collided with the body~\cite{werner1996}
 
 In this work, we consider trajectories about asteroid 4769 Castalia.
-The shape model uses Doppler radar images to Castalia obstained at the Arecibo Observatory in 1989~\cite{hudson1994,neese2004}.
+Doppler radar images, obtained at the Arecibo Observatory in 1989, are used to determine a shape model of Castalia~\cite{hudson1994,neese2004}.
 We use the estimated rotation period of \SI{4.07}{\hour} with a nominal density of \SI{2.1}{\gram\per\centi\meter\cubed}~\cite{scheeres1996}.
@@
 
-Mention that our model uses only 1024 faces for speed
-
-Show the plot of the equilibrium position as a function of the number of faces and show that it's where the knee in the curve exists
-
 \subsection{Spacecraft Equations of Motion}\label{sec:sc_eoms}
@@
 As is typical in the three-body problem, the equations of motion are usually represented in a uniformly rotating frame aligned with the two primaries.
-Similarily, the equations of motion about an asteroid are also defined in a body-fixed frame with uniform rotation.
+Similarly, the equations of motion about an asteroid are also defined in a body-fixed frame with uniform rotation.
 In this reference frame, the gravitational potential field is time invariant and only a function of the position of the particle.
-In addition, since the rotational rate of the asteroid is constant the equations of motion are time invariant.
+In addition, since the rotational rate of the asteroid is constant, the equations of motion are time invariant.
 Finally, the use of the rotating reference frame allows for much greater insight into the dynamic structure of the behavior around the asteroid.
@@
 \end{align}
-where \( \vecbf{\Omega} \) is the instaneous angular velocity vector of the asteroid represented in the body-fixed frame, \( \vecbf{r} \) is the position of the particle in the body-fixed frame, and \( U_{\vecbf{r}} \) is the gradient of the gravitational potential~\cite{scheeres2012a}.
+where \( \vecbf{\Omega} \) is the instantaneous angular velocity vector of the asteroid represented in the body-fixed frame, \( \vecbf{r} \) is the position of the particle in the body-fixed frame, and \( U_{\vecbf{r}} \) is the gradient of the gravitational potential~\cite{scheeres2012a}.
 We assume that the asteroid rotates at a uniform rate, \( \norm{\vecbf{\Omega}} = \omega \), about the axis of the maximum moment of inertia, \( \vecbf{\Omega} = \omega \hat{\vecbf{z} }\).
@@
 
-We assume that in our problem we are modelling a spacecraft rather than a massless particle.
 In this situation, the state is defined as \( \vecbf{x} = \begin{bmatrix}\vecbf{r} &\vecbf{v} \end{bmatrix}^T\) with \(\vecbf{r} = \begin{bmatrix} x & y & z \end{bmatrix}^T \in \R^{3\times1}\) and \(\vecbf{v}= \begin{bmatrix} \dot{x} & \dot{y} & \dot{z} \end{bmatrix}^T \in \R^{3\times1}\) representing the position and velocity with respect to the body-fixed frame, respectively.
 We further assume that our spacecraft is capable of exerting a translational force, \( \vecbf{u} \in \R^{3\times1} \), in any direction, while subject to a maximum magnitude constraint.
-This is typical of many spacecraft which offer full rotational freedom and can direct a maximum, and potentially varying, thrust in any direction.
+This is typical of many spacecraft which offer full rotational freedom and can direct a potentially varying thrust in any direction.
 The equations of motion may be rewritten in state space form as
@@
 Since Castalia is a uniformly rotating asteroid, the equations of motion are time invariant when represented in the body-fixed frame.
-In addition, there exists an integral of motion, or a conserved quantity, the is constant for all motion of a particle, absent any other perturbing forces.
+In addition, there exists an integral of motion, or a conserved quantity, that is constant for all motion of a particle.
 The Jacobi constant, \( J (\vecbf{r} , \vecbf{v} ) \), is given by
@@
 Just as in the three-body problem, the Jacobi constant in~\cref{eq:jacobi} divides the phase space into distinct realms of possible motion.
-Similarly, there exist in general four equilibrium points and also their associated stable and unstable manifolds~\cite{scheeres1996,scheeres1994}.
-The properties of these manifolds play a critical role in the dynamics of trajecotries in their vicinity.
+Similarly, there exist, in general, four equilibrium points and also their associated stable and unstable manifolds~\cite{scheeres1996,scheeres1994}.
+The properties of these manifolds play a critical role in the dynamics of trajectories in their vicinity.
 
@@
 Typical optimal control methods, including both indirect and direct based methods, are highly dependent on an accurate initial guess.
-For indirect optimization, which is based on the calclus of variations, this results in the well-known two-point boundary value problem.
+For indirect optimization, which is based on the calculus of variations, this results in the well-known two-point boundary value problem.
 Insight into the problem or insight by the designer is usually required to determine appropriate initial costates that will converge to the optimal solution and satisfy the desired constraints.
-To avoid this issue, we utilize the concept of the reachiblity set on a lower dimensional \Poincare section.
+To avoid this issue, we utilize the concept of the reachability set on a lower dimensional \Poincare section.
 By repeatedly constructing the reachability set we can achieve general transfers by determining set intersections on the \Poincare section.
@@
 Reachability theory has been applied to collision avoidance and safety planning in aerospace systems~\cite{holzinger2009,holzinger2011b}.
-The theory supporting reachabiilty analysis is directly derivable from optimal control theory~\cite{varaiya2000,lygeros2004}.
+The theory supporting reachability analysis is directly derivable from optimal control theory~\cite{varaiya2000,lygeros2004}.
 Analytic, computation of reachability sets is only possible for a small class of potential systems.
@@
 The \Poincare section is chosen in a manner similar to the previous work in both the three-body problem as well analysis performed around asteroids to determine periodic orbits.
-Analysis in the three-body problem relies heaviliy on symmetries in the force fields.
+Analysis in the three-body problem relies heavily on symmetries in the force fields.
 However, in our system model the gravitational potential, given by~\cref{eq:potential}, has no symmetries.
@@
 The constraints \( m_2, m_3, m_4 \) are used to define a direction on the \Poincare section.
-We approximate the entire reachable set by discretizing the space of angles \(\phi_1, \phi_2, \phi_3 \).
+We approximate the entire reachable set by discretization  over the space of angles \(\phi_1, \phi_2, \phi_3 \).
 By convention we assume that the angles lie in the following range
@@
 This constraint assumes that the control thrust may be orientated in any direction yet the thrust is variable but limited.
-The goal is to determine the control history \( \vecbf{u}(t) \) such that teh cost function~\cref{eq:cost} is minimized while subject to the equations of motion~\cref{eq:body_eoms} and the constraints~\cref{eq:control_constraint,eq:terminal_constraints}.
+The goal is to determine the control history \( \vecbf{u}(t) \) such that the cost function~\cref{eq:cost} is minimized while subject to the equations of motion~\cref{eq:body_eoms} and the constraints~\cref{eq:control_constraint,eq:terminal_constraints}.
 
@@
 
-We can redefine the optimal control in terms of the costate by rewritting the necessary condition as
+We can redefine the optimal control in terms of the costate by rewriting the necessary condition as
 \begin{align*}
@@
 \end{align*}
-We use this along with the control constraint to solve for the Lagrange multipler \( \mu \)
+We use this along with the control constraint to solve for the Lagrange multiplier \( \mu \)
 \begin{align*}
@@
 In this analysis, we assume \( u_m = \SI{0.1}{\milli\meter\per\second\squared}\) which is equivalent to a thrust of approximately \SI{100}{\milli\newton} for a \SI{1000}{\kilo\gram} spacecraft.
-This amount of thrust is typical of many current ion or hall effect thrusters and is in operation in several current missions (cite Goebels Fundamentals of electric propulsion and Dawn thruster paper by choueiri2009new).
+This amount of thrust is typical of many current ion or hall effect thrusters and is in operation in several current missions~\cite{goebel2008 ,choueiri2009}.
 
@@
 The reachability set is generated on the lower dimensional \Poincare section and is composed of the terminal states in the \( \parenth{x,z,\dot{x},\dot{z} } \) space.
-We approximate the reachability set by discritizing each of the angles \( \phi_1, \phi_2 , \phi_3 \) into ten discrete steps. 
+We approximate the reachability set by discretization of each of the angles \( \phi_1, \phi_2 , \phi_3 \) into ten discrete steps. 
 This results in a total of \(10^3\) trajectories which approximate the reachability set on the \Poincare section.
@@
         \caption{\( x \) vs. \( \dot{x} \) \Poincare section} \label{fig:poincare_xvsxdot} 
-    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \end{subfigure}~
     \begin{subfigure}[htbp]{0.45\textwidth} 
@@
 The first stage of the transfer is represented by the magenta markers in~\cref{fig:poincare_section}.
-From~\cref{fig:poincare_xvsxdot}, we can see that the reachablity set has grown in the \( \dot{x} \) dimension but has not been enlarged much in the \( x \) direction.
-Similarily,~\cref{fig:poincare_zvszdot} shows an increase in the \( \dot{z} \) component while still maintaining the \( z = 0 \) terminal constraint.
+From~\cref{fig:poincare_xvsxdot}, we can see that the reachability set has grown in the \( \dot{x} \) dimension but has not been enlarged much in the \( x \) direction.
+Similarly,~\cref{fig:poincare_zvszdot} shows an increase in the \( \dot{z} \) component while still maintaining the \( z = 0 \) terminal constraint.
 From the reachability set, we chose a trajectory and terminal state which minimizes a distance metric \( d(\vecbf{x}_f,\vecbf{x}_t) \) to the desired target
@@
         \caption{ \( \phi_1 \)} \label{fig:phi1} 
-    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \end{subfigure}~
     \begin{subfigure}[htbp]{0.3\textwidth} 
@@
         \caption{\( \phi_2 \)} \label{fig:phi2} 
-    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \end{subfigure}~
     \begin{subfigure}[htbp]{0.3\textwidth} 
@@
 Since the reachability set does not include the target we use the minimum state from the first stage to initialize another reachability computation.
-Once again we compute the reachability set by discritizing the space on the \Poincare section using the angles \( \phi_i \).
+Once again we compute the reachability set by discretization of the angles \( \phi_i \) on the \Poincare section.
 This second stage, represented by the green markers in~\cref{fig:poincare_section,fig:phi_distance}, further increase the \( x \) component but does not reach the target orbit.
@@
         \caption{Equatorial view of transfer} \label{fig:trajectory_up} 
-    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \end{subfigure}~
     \begin{subfigure}[htbp]{0.45\textwidth} 
@@
         \caption{Out of plane view} \label{fig:trajectory_3d} 
-    \end{subfigure}~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. %(or a blank line to force the subfigure onto a new line) 
+    \end{subfigure}~ 
     \caption{Complete transfer trajectory}
@@
 \end{figure}
-It is interesting to note the while both the initial and target periodic orbit lie in the equatorial plane, the reachablity trajectories show a relatively large out of plane component during the transfers.
+It is interesting to note the while both the initial and target periodic orbit lie in the equatorial plane, the reachability trajectories show a relatively large out of plane component during the transfers.
 In spite of this out of plane movement, the reachability set approaches and meets the target orbit. 
@@
 \end{figure}
-\Cref{fig:control} shows the control input required during the manuever.
+\Cref{fig:control} shows the control input required during the maneuver.
 The transfers show a large out of plane movement for a planar transfer
@@
 The use of the \Poincare section allows for trajectory design on a lower dimensional space and is an extension of its well-known use in the analysis of periodic orbits.
-We use an indirect optimal control formulation to incorporate a control magnitude contraint and several terminal state constraints.
+We use an indirect optimal control formulation to incorporate a control magnitude constraint and several terminal state constraints.
 Utilizing the reachability set alleviates the need to determine accurate initial conditions that allow for convergence of the optimal solution.
-In addition, the use of the polyhedron gravitational model gives simple method of extending this work to any small body that also posseses a defined shape model.
+In addition, the use of the polyhedron gravitational model gives simple method of extending this work to any small body that also possesses a defined shape model.
 

### 2016-08-10 manuscript.tex
Correct some typos and clarity issues

@@
 These transfers are computed through the use of a reachability set generated on a lower dimensional \Poincare surface.
+Complex, long duration transfer trajectories are highly sensitive to the initial guess and generally have a small region of convergen.
 Computation of the reachable set alleviates the need to generate an accurate initial guess for optimization.
+From the reachable set, we chose a trajectory which minimizes a metric towards the desired target.
 Successive computation of the reachable set allows for the design of general transfer trajectories.
@@
 In this situation, the state is defined as \( \vecbf{x} = \begin{bmatrix}\vecbf{r} &\vecbf{v} \end{bmatrix}^T\) with \(\vecbf{r} = \begin{bmatrix} x & y & z \end{bmatrix}^T \in \R^{3\times1}\) and \(\vecbf{v}= \begin{bmatrix} \dot{x} & \dot{y} & \dot{z} \end{bmatrix}^T \in \R^{3\times1}\) representing the position and velocity with respect to the body-fixed frame, respectively.
-We further assume that our spacecraft is capable of exerting a translational force, \( \vecbf{u} \in \R^{3\times1} \), in any direction, while subject to a maximum magnitude constraint.
-This is typical of many spacecraft which offer full rotational freedom and can direct a potentially varying thrust in any direction.
+We further assume that our spacecraft is capable of exerting a translational acceleration, \( \vecbf{u} \in \R^{3\times1} \), in any direction, while subject to a maximum magnitude constraint.
+This is typical of many spacecraft which offer full rotational freedom and can direct a potentially varying force or acceleration in any direction.
 The equations of motion may be rewritten in state space form as
@@
 The theory supporting reachability analysis is directly derivable from optimal control theory~\cite{varaiya2000,lygeros2004}.
-Analytic, computation of reachability sets is only possible for a small class of potential systems.
-Here, we use numerical methods to solve an optimal control problem.
-The solution of this optimal control problem approximates a single solution that lies on the reachable set.
+Analytic computation of reachability sets is only possible for a small class of potential systems.
+Here, we use numerical methods to solve a related optimal control problem, which approximates a single solution that lies on the reachable set.
 \begin{figure}
@@
 However, in our system model the gravitational potential, given by~\cref{eq:potential}, has no symmetries.
-In spite of this, it is still possible to determine periodic solutions through the application of a \Poincare map with surface of section chosen normal to surface in the phase space~\cite{scheeres2000}.
+In spite of this, it is still possible to determine periodic solutions through the application of a \Poincare map with surface of section chosen normal to a surface in the phase space~\cite{scheeres2000}.
 For a periodic orbit, the trajectories will intersect the \Poincare section at two distinct points every half orbit.
@@
 We use the cost function \( J \) to define a distance metric on the \Poincare section.
-Maximization of \( J \), or the minimization of \( -J \), along various directions on the \Poincare section allows us to generate the larges reachability set under the bounded control input.
+Maximization of \( J \), or the minimization of \( -J \), along various directions on the \Poincare section allows us to generate the largest reachability set under the bounded control input.
 
@@
 Following convention, the \Poincare map is defined as the map from one transversal crossing of the surface \( y = 0\) to the next.
-Using the method of Reference~\citenum{scheeres2000}, we are able to remove \( y \) and \( \dot{y} \), creating a four-dimensional map.
-The \Poincare section, \( \Sigma \) then becomes
+Using the method of Reference~\citenum{scheeres2000}, we remove \( y \) and \( \dot{y} \) from consideration and create a four-dimensional map.
+The \Poincare section, represented by \( \Sigma \), then becomes
 \begin{align}\label{eq:poincare_section}
@@
 \end{align}
-We use this section to compute periodic orbits that serve as the initial and target of our transfer.
+We use this section to compute periodic orbits that serve as the initial and target states of our transfer.
 In addition, this section serves as a lower dimensional space upon which we approximate the reachability set.
@@
     J = -\frac{1}{2} \left( \vecbf{x}(t_f) - \vecbf{x}_{n}(t_f)\right)^T 
-    \begin{bmatrix}
-        1 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 1 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 1 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 0 \\
-        0 & 0 & 0 & 0 & 0 & 1 \\
-    \end{bmatrix}
+    Q
     \left( \vecbf{x}(t_f) - \vecbf{x}_{n}(t_f)\right) ,
@@
 where \( \vecbf{x}_n(t_f) \) is the final state of a control-free trajectory, while the term \( \vecbf{x}(t_f)\) is the final state of a trajectory under the influence of the control input.
+We use the matrix \( Q = \text{diag} \begin{pmatrix} 1 & 0 & 1 & 1 & 0 &1 \end{pmatrix} \in \R^{6 \times 6}\) to represent the mapping onto \( \Sigma \).
 Maximization of the distance between \( \vecbf{x}_n \) and \(\vecbf{x} \), on the \Poincare section defined in~\cref{eq:poincare_section}, is equivalent to the minimization of \( J \) defined in~\cref{eq:cost}.
@@
 In addition, we use the terminal constraints to define a specific direction along which we seek to minimize the cost~\cref{eq:cost}.
-Since the \Poincare section is four-dimensional we parameterize a direction in \( \R^4 \)  using three angles \( \phi_1, \phi_2 , \phi_3 \) to define the terminal constraints
+Since the \Poincare section is four-dimensiona, we parameterize a direction in \( \R^4 \)  using three angles \( \phi_1, \phi_2 , \phi_3 \).
+The terminal constraints are given as
 \begin{align}\label{eq:terminal_constraints}
     \begin{split}
-        m_1 &= y = 0 \\
+        m_1 &= y = 0 , \\
         m_2 &= \parenth{\sin \phi_{1_{d}}} \parenth{ x_1^2 + x_2^2 + x_3^2 + x_4^2} - x_1^2 = 0, \\
         m_3 &= \parenth{\sin \phi_{2_{d}}} \parenth{ x_2^2 + x_3^2 + x_4^2} - x_2^2 = 0, \\
-        m_4 &= \parenth{\sin \phi_{3_{d}}} \parenth{ 2 x_3^2 + 2 x_3 \sqrt{x_4^2 + 2 x_4^2}} - x_3 - \sqrt{x_4^2 + x_3^2} = 0. 
+        m_4 &= \parenth{\sin \phi_{3_{d}}} \parenth{ 2 x_3^2 + 2 x_3 \sqrt{x_4^2 + 2 x_4^2}} - x_3 - \sqrt{x_4^2 + x_3^2} = 0 ,
     \end{split}
 \end{align}
-We make use of the difference states \( \parenth{x_1, x_2 ,x_3, x_4 }\) which are defined as
+where we make use of the difference states \( \parenth{x_1, x_2 ,x_3, x_4 }\) defined as
 \begin{align}\label{eq:diff_states}
@@
 The constraints \( m_2, m_3, m_4 \) are used to define a direction on the \Poincare section.
+\Cref{eq:diff_states} represents the difference between our controlled and uncontrolled trajectory on the \Poincare section.
 We approximate the entire reachable set by discretization  over the space of angles \(\phi_1, \phi_2, \phi_3 \).
@@
 such that we parameterize all directions on the three sphere, \(\S^3\).
-Finally, we also incorporate a control thrust magnitude constraint given by
+Finally, we also incorporate a control acceleration magnitude constraint given by
 \begin{align}\label{eq:control_constraint}
@@
 \end{align}
-where \( u_m \) is the maximum thrust magnitude.
-This constraint assumes that the control thrust may be orientated in any direction yet the thrust is variable but limited.
+where \( u_m \) is the maximum acceleration possible by the propulsion system.
+This constraint assumes that the control acceleration may be orientated in any direction yet the acceleration magnitude is variable but bounded.
 The goal is to determine the control history \( \vecbf{u}(t) \) such that the cost function~\cref{eq:cost} is minimized while subject to the equations of motion~\cref{eq:body_eoms} and the constraints~\cref{eq:control_constraint,eq:terminal_constraints}.
@@
 In addition, we implement a multiple shooting method which sub-divides the the entire trajectory into small sub-intervals~\cite{stoer2013}.
-We incorporate additional interior constraints to ensure a continuous trajectory at the patch points between the sub-intervals.
-The multiple shooting method reduces the sensitivity of the terminal states to the initial conditions and alleviates many of the issues of single shooting approaches.
+The multiple shooting method reduces the sensitivity of the terminal states to the initial conditions.
+Using a shorter time interval alleviates many of the issues of single shooting approaches, which suffer from convergence difficulties near the optimal solution.
+To ensure a continuous trajectory we incorporate additional constraints
+\begin{align}\label{sec:interior_constraints}
+    \vecbf{x}_{m-1}^{-} &= \vecbf{x}_m^{+} , \\
+    \vecbf{\lambda}_{m-1}^{-} &= \vecbf{\lambda}_m^{+},
+\end{align}
+which ensure that both the state and costate are continuous at the patch point between segment \( m-1 \) and \( m\).
 
@@
 We instead model the control input as a generic acceleration vector in the body-fixed asteroid frame. 
-The thrust magnitude constraint in~\cref{eq:control_constraint} is chosen to emulate a physically realizable thruster system.
+The acceleration magnitude constraint in~\cref{eq:control_constraint} is chosen to emulate a physically realizable thruster system.
 In this analysis, we assume \( u_m = \SI{0.1}{\milli\meter\per\second\squared}\) which is equivalent to a thrust of approximately \SI{100}{\milli\newton} for a \SI{1000}{\kilo\gram} spacecraft.
-This amount of thrust is typical of many current ion or hall effect thrusters and is in operation in several current missions~\cite{goebel2008 ,choueiri2009}.
+This amount of thrust is typical of many current ion or hall effect thrusters~\cite{goebel2008 ,choueiri2009}.
 
@@
 Rather than using the full \num{4092} face model we reduce the number of faces to \num{1024}. 
-This greatly speeds up the computation with only a small difference in the potential field or shape model.
+This greatly speeds up the computation with only a small difference in the gravitational field.
 
-We first compute the reachability set originating from the initial periodic orbit at \( \vecbf{x}_i\) for a fixed time of flight and bounded control magnitude as defined preivously.
+We first compute the reachability set originating from the initial periodic orbit at \( \vecbf{x}_i\) for a fixed time of flight and bounded control magnitude as defined previously.
 Since the target periodic orbit also lies in the equatorial plane, we augment~\cref{eq:terminal_constraints} with an additional constraint \( m_5 = z = 0\) to ensure that the trajectories remain in the equatorial plane.
+Similarly, we also add another Lagrange multipler, \( \beta \in \R^{5 \times 1}\), to account for this addiitonal terminal constraint.
 The reachability set is computed by solving the two-point boundary value problem using a multiple shooting algorithm to satisfy the necessary conditions in~\cref{eq:necc_conditions}.
@@
     \end{subfigure}
-    \caption{\Poincare section visualization}
-    \label{fig:poincare_section} 
+    \caption{\Poincare section visualization \label{fig:poincare_section}}
 \end{figure}
@@
 
-The trajectory which minimizes \( d \) is indicated by the red marker in~\cref{fig:poincare_section ,fig:phi_distance}.
+The trajectory which minimizes \( d \) is indicated by the red marker in~\cref{fig:poincare_section,fig:phi_distance}.
 Since the reachability set does not include the target we use the minimum state from the first stage to initialize another reachability computation.
 Once again we compute the reachability set by discretization of the angles \( \phi_i \) on the \Poincare section.
-This second stage, represented by the green markers in~\cref{fig:poincare_section,fig:phi_distance}, further increase the \( x \) component but does not reach the target orbit.
-As a result, a third stage is generated in a similar manner and shown by the green markers in~\cref{fig:poincare_section ,fig:phi_distance}.
-We can see in~\cref{fig:poincare_section} that the reachability set of the third stage includes both the \( x \) and \( z\) of the target periodic orbit.
+This second stage, represented by the blue markers in~\cref{fig:poincare_section,fig:phi_distance}, further increase the \( x \) component but does not reach the target orbit.
+As a result, a third stage is generated in a similar manner and shown by the green markers in~\cref{fig:poincare_section,fig:phi_distance}.
+We can see in~\cref{fig:poincare_section} that the reachability set of the third stage includes both the \( x \) and \( z\) components of the target periodic orbit.
 At the same time there is a relatively large difference between the \( \dot{x} \) and \( \dot{z} \) components of the third stage and the target orbit.

### 2016-08-11 manuscript.tex
Add some corrections from Christine

@@
     \thanks{Doctoral Student, \href{mailto:skulumani@gwu.edu}{skulumani@gwu.edu}. Student AIAA Member.}
-  \ and Taeyoung Lee\thanksibid{2}\thanks{Associate Professor, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}. AIAA Member}\\
+  \ and Taeyoung Lee\thanksibid{2}\thanks{Associate Professor, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}. AIAA Member.}\\
   {\normalsize\itshape
@@
 % Motivation for missions/studying asteroids
-Small solar system bodies, such as asteroids and comets, are of significant interest to the scientific community.
-These small bodies offer great insight into the early formation of the solar system.
+Small solar system bodies, such as asteroids and comets, are of significant interest to the scientific community; these small bodies offer great insight into the early formation of the solar system.
 This insight offers additional detail into the formation of the Earth and also the probable formation of other planetary bodies.
 Of particular interest are those near-Earth asteroids (NEA) which inhabit heliocentric orbits in vicinity of the Earth.
-These easily accessible bodies provide attractive targets to support space industrialization, mining operations, and scientific missions..
-NEAs potentially contain many materials useful for propulsion, construction, semiconductors, precious and strategic metals~\cite{ross2001}.
-In addition, these NEAs are also of concern for their potential to impact the Earth~\cite{wie2008}.
-Asteroids and comets are the greatest threat to future civilizations and as a result there is a focused effort to mitigate these risks.
+These easily accessible bodies provide attractive targets to support space industrialization, mining operations, and scientific missions.
+NEAs potentially contain many materials such as those useful for propulsion, construction, or for use in semiconductors.
+Also, many bodies contain highly profitable materials, such as precious or strategic metals~\cite{ross2001}.
+In addition, these NEAs are also of concern for their potential to impact the Earth.
+Asteroids and comets are the greatest threat to future civilizations and as a result there is a focused effort to mitigate these risks~\cite{wie2008}.
 In spite of the great interest in asteroids, the operation of spacecraft in their vicinity is a challenging problem.
@@
 The dynamic environment around asteroids is strongly perturbed and challenging for analysis and mission operation.
-Due to their small size, resulting in a low gravitational attraction, asteroids have irregular shapes or potentially chaotic spin states.
-Furthermore, due to their low mass other non-gravitational effects, such as solar radiation pressure or third-body effects, become much more significant.
-As a result, the orbital environment is in general quite complex and it is difficult to generate analytical insights.
+Due to their low mass, which results in a low gravitational attraction, asteroids may have irregular shapes and potentially chaotic spin states.
+Furthermore, since the magnitude of the gravitational attraction is relatively small non-gravitational effects, such as solar radiation pressure or third-body effects, become much more significant.
+As a result, the orbital environment is generally quite complex and it is difficult to generate analytical insights.
 
@@
 The application of optimal control methods for orbital trajectory design is nontrivial.
-In order to implement any optimization method a sufficiently accurate ``initial guess'' is required.
-Frequently, insight into the problem or intuition on the part of the designer is often required to determine initial conditions that will converge to the optimal solution.
+Frequently, insight into the problem or intuition on the part of the designer is required to determine initial conditions that will converge to the optimal solution.
 However, the asteroid system dynamics are nonlinear and exhibit chaotic behaviors.
@@
 The motion of particles around asteroids is modeled using the restricted full two-body problem.
-This model has many similarities with the restricted three body problem, and much of the theory developed in the three-body problem is also applicable.
+This model has many similarities with the restricted three body problem, and much of the theory developed for the three-body problem is also applicable.
 The similarity of the three-body problem to motion around asteroids allows for much of the same theory to be applied to the asteroid problem~\cite{mondelo2010,herrera2014}.
@@
 Our approach avoids the difficulties in selecting an appropriate initial guess for optimization.
-Instead, we utilize the concept of the reachability set to enable a simple methodology of selecting initial conditions to achieve general orbital transfers.
+We instead utilize the concept of the reachability set to enable a simple methodology of selecting initial conditions to achieve general orbital transfers.
 Given an initial condition and fixed time horizon, the reachable set is the set of states attainable, subject to the operational constraints of the spacecraft.
-We calculate the reachable set on a lower dimensional \Poincare section which allows a 
-In addition, the generation of the reachable set allows for a more systematic method of determining initial conditions and eases the burden on the designer.
+We calculate the reachable set on a lower dimensional \Poincare section. 
+The generation of the reachable set allows for a more systematic method of determining initial conditions and eases the burden on the designer.
 This simple methodology allows for extended transfer trajectories which iteratively approach a desired target orbit.
@@
 Approximations are possible by truncating the infinite order series to fixed set of coefficients, with the most important terms corresponding to the second order and degree~\cite{scheeres1994}. 
-The approximation error is generally small given a sufficient amount of terms. 
 However, when evaluated close to the body the series expansion will diverge and is no longer accurate. 
+Therefore, the spherical harmonic representation is not ideal for landing trajectories or those passing close to the surface.
 
@@
 A polyhedral model of the surface of an asteroid can be determined from remote optical or radar sensors.
-The faces of the polyhedron can be large or small and allows for fine detail such as depression, craters, ridges, or interior voids.
+The faces of the polyhedron can be large or small and allow for fine detail such as depression, craters, ridges, or interior voids.
 In addition, there is no requirement for the body to be modeled at a uniformly high resolution so small details can be incorporated with minimal cost.
@@
 We represent the gravitational potential of the asteroid using a polyhedron gravitation model.
-This model is composed of a polyhedron, a three-dimensional solid body, which is defined by a series of vectors in the body-fixed frame.
+This model is composed of a polyhedron, a three-dimensional solid body, that is defined by a series of vectors in the body-fixed frame.
 The vectors define vertices in the body-fixed frame as well as planar faces which compose the surface of the asteroid.
@@
 Only the body-fixed vectors, and their associated topology, is required to define the exterior gravitational model.
-References~\citenum{werner1994} and~\citenum{werner1997} give a detailed derivation of the polyhedron model.
+References~\citenum{werner1994} and~\citenum{werner1996} give a detailed derivation of the polyhedron model.
 Here, we summarize the key developments and equations required for implementation.
@@
 They are both solely functions of the vertices and edges of the polyhedral shape model and are computed once and stored.
-Once a position vector \( \vecbf{r} \) is defined then the scalars given in~\cref{eq:edge_factor,eq:face_factor} can be computed for each face and edge.
+Once a position vector \( \vecbf{r} \) is defined, the scalars given in~\cref{eq:edge_factor,eq:face_factor} can be computed for each face and edge.
 Finally,~\cref{eq:potential} is used to compute the gravitational potential on the spacecraft.
@@
 The shape model is composed of \num{4092} triangular faces and a rendering of the asteroid is provided in~\cref{fig:castalia_3d}.
-In addition, we also show a contour plot of the radius of Castlia in~\cref{fig:radius_contour}.
+In addition, we show a contour plot of the radius of Castlia in~\cref{fig:radius_contour}.
 \begin{figure}
@@
 To avoid this issue, we utilize the concept of the reachability set on a lower dimensional \Poincare section.
-By repeatedly constructing the reachability set we can achieve general transfers by determining set intersections on the \Poincare section.
+By repeatedly constructing the reachability set, we can achieve general transfers by determining set intersections on the \Poincare section.
 This alleviates the need to determine an accurate initial guess while offering some insight into the dynamics of neighboring trajectories
@@
 The \Poincare section is chosen in a manner similar to the previous work in both the three-body problem as well analysis performed around asteroids to determine periodic orbits.
-Analysis in the three-body problem relies heavily on symmetries in the force fields.
-However, in our system model the gravitational potential, given by~\cref{eq:potential}, has no symmetries.
-In spite of this, it is still possible to determine periodic solutions through the application of a \Poincare map with surface of section chosen normal to a surface in the phase space~\cite{scheeres2000}.
+Typically, analysis for the three-body problem relies heavily on symmetries in the force fields.
+However, in our system model, the gravitational potential, given by~\cref{eq:potential}, has no symmetries.
+In spite of this, it is still possible to determine periodic solutions through the application of a \Poincare map with the surface of section chosen normal to a surface in the phase space~\cite{scheeres2000}.
 For a periodic orbit, the trajectories will intersect the \Poincare section at two distinct points every half orbit.
@@
 \end{align}
-The constraint \( m_1 = 0 \) ensures that the terminal states lies on the \Poincare section.
+The constraint \( m_1 = 0 \) ensures that the terminal state lies on the \Poincare section.
 The constraints \( m_2, m_3, m_4 \) are used to define a direction on the \Poincare section.
@@
 % How do you solve the optimal control problem
-We apply a standard calculus of variations approach to solve our optimal control problem~\cite{bryson2002}.
+We apply a standard calculus of variations approach to solve our optimal control problem~\cite{bryson1975}.
 Using the Euler-Lagrange equations we arrive at the necessary conditions for optimality
@@
 \end{figure}
-It is interesting to note the while both the initial and target periodic orbit lie in the equatorial plane, the reachability trajectories show a relatively large out of plane component during the transfers.
+It is interesting to note that while both the initial and target periodic orbit lie in the equatorial plane, the reachability trajectories show a relatively large out of plane component during the transfers.
 In spite of this out of plane movement, the reachability set approaches and meets the target orbit. 

### 2016-08-11 manuscript.tex
Fix some more typos

@@
 These transfers are computed through the use of a reachability set generated on a lower dimensional \Poincare surface.
-Complex, long duration transfer trajectories are highly sensitive to the initial guess and generally have a small region of convergen.
+Complex, long duration transfer trajectories are highly sensitive to the initial guess and generally have a small region of convergence.
 Computation of the reachable set alleviates the need to generate an accurate initial guess for optimization.
-From the reachable set, we chose a trajectory which minimizes a metric towards the desired target.
-Successive computation of the reachable set allows for the design of general transfer trajectories.
+From the reachable set, we chose a trajectory which minimizes a distance metric towards the desired target.
+Successive computation of the reachable set allows for the design of general transfer trajectories which iteratively approach the target.
 We demonstrate this method by determining a transfer trajectory about the asteroid 4769 Castalia.
@@
 Due to their low mass, which results in a low gravitational attraction, asteroids may have irregular shapes and potentially chaotic spin states.
-Furthermore, since the magnitude of the gravitational attraction is relatively small non-gravitational effects, such as solar radiation pressure or third-body effects, become much more significant.
+Furthermore, since the magnitude of the gravitational attraction is relatively small, non-gravitational effects, such as solar radiation pressure or third-body effects, become much more significant.
 As a result, the orbital environment is generally quite complex and it is difficult to generate analytical insights.
@@
 This results in a cumbersome gravity field model that requires additional constraints to ensure continuity and validity at the radius of the circumscribing sphere~\cite{werner1994 ,werner1996}.
-Instead, we model the asteroid as a constant-density polyhedron and avoid the issues of the harmonic expansion while enabling several other useful advantages.
+Instead, we model the asteroid as a constant-density polyhedron and avoid the issues of the harmonic expansion.
 
@@
 The motion of particles around asteroids is modeled using the restricted full two-body problem.
-This model has many similarities with the restricted three body problem, and much of the theory developed for the three-body problem is also applicable.
-The similarity of the three-body problem to motion around asteroids allows for much of the same theory to be applied to the asteroid problem~\cite{mondelo2010,herrera2014}.
+This model has many similarities with the restricted three body problem, and much of the theory developed for the three-body problem is also applicable~\cite{mondelo2010,herrera2014}.
 In this paper, we extend the design method developed in the three-body problem to motion about asteroids~\cite{kulumani2015}.
@@
 Each edge is a member of two faces and has an outward pointing edge normal vector, given in~\cref{eq:edge_normal}, perpendicular to both the edge and the face normal.
-For the edge connecting the vectors \( \vecbf{v}_1 \) and \( \vecbf{v}_2 \) which are shared between the faces \(A\) and \( B\), the per edge dyad is given by
+For the edge connecting the vectors \( \vecbf{v}_1 \) and \( \vecbf{v}_2 \), which are shared between the faces \(A\) and \( B\), the per edge dyad is given by
 \begin{align}\label{eq:edge_dyad}
@@
 \end{align}
-The edge dyad, \( \vecbf{E}_e \), is defined for each edge and a function of the two adjacent faces meeting at the edge.
-The face dyad, \( \vecbf{F}_f \), is defined for each face and is a function of the face normal vector.
+The edge dyad, \( \vecbf{E}_e \), is defined for each edge and is a function of the two adjacent faces meeting at the edge.
+The face dyad, \( \vecbf{F}_f \), is defined for each face and is a function of the face normal vectors.
 
-Let \( \vecbf{r}_i \) be the vector from the spacecraft to the vertex \( \vecbf{v}_i \) and it's length is \( r_i = \norm{\vecbf{r}_i} \).
+Let \( \vecbf{r}_i \) be the vector from the spacecraft to the vertex \( \vecbf{v}_i \) and it's length is given by \( r_i = \norm{\vecbf{r}_i} \).
 The per-edge factor \( L_e \), for the edge connecting vertices \( \vecbf{v}_i \) and \( \vecbf{v}_j \), with a constant length \( e_{ij} \) is
@@
 \begin{align}\label{eq:potential}
-    U(\vecbf{r}) &= 1\frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f
+    U(\vecbf{r}) &= 1\frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f ,
 \end{align}
-where \( \vecbf{r}_e, \vecbf{r}_f \) is the vector from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
-Furthermore we can use these definitions to define the attraction, gravity gradient matrix, and Laplacian are defined as
+where \( \vecbf{r}_e\) and \(\vecbf{r}_f \) are the vectors from the spacecraft to any point on the respective edge or face, \( G\) is the universal gravitational constant, and \( \sigma \) is the constant density of the asteroid.
+Furthermore we can use these definitions to define the attraction, gravity gradient matrix, and Laplacian as
 \begin{align}
@@
     \begin{tikzpicture}[scale=\tikzscale]
-        \coordinate [label=left:\textcolor{black}{\large \(\vec{x}_0\)}] (x0) at (-1,-2);
-        \coordinate [label=below:\textcolor{black}{\large  \(\vec{x}_n\)}] (xn) at (1,1);
+        \coordinate [label=left:\textcolor{black}{\large \(\vecbf{x}_0\)}] (x0) at (-1,-2);
+        \coordinate [label=below:\textcolor{black}{\large  \(\vecbf{x}_n\)}] (xn) at (1,1);
         \coordinate [label=left:\textcolor{black}{\large  \(\Sigma\)}] (sigma) at (-4,3);
@@
         \coordinate [label=right:\textcolor{black}{}] (f1) at (5,-2);
-        \coordinate [label=below:\textcolor{black}{\large  \(\phi(t,\vec{x}_0)\)}] (f2) at (2,-5);
+        \coordinate [label=below:\textcolor{black}{\large  \(\psi(t,\vecbf{x}_0)\)}] (f2) at (2,-5);
         \coordinate [label=right:\textcolor{black}{}] (f3) at (-4,-4);
@@
         \draw ($(xn) + (1,0)$) arc [start angle=0,end angle=45, radius=1];
-        \node [draw=none] at (2.4,1.5) {\Large \(\theta_d\)};
+        \node [draw=none] at (2.4,1.5) {\Large \(\phi_d\)};
         \draw [decorate,decoration={brace,amplitude=5pt},rotate=45] (xn) -- ($(xn) + (2,0)$);
@@
 \Cref{fig:reachability_set} illustrates this methodology.
-Without any control input, the trajectories will intersect the \Poincare section at \( \vecbf{x}_n\).
-The addition of a control input allows the spacecraft to depart from the natural dynamics and intersect the section at another location.
+Without any control input, the trajectories will follow the system dynamics, \( \psi(t, \vecbf{x}_0 ) \) and intersect the \Poincare section at \( \vecbf{x}_n\).
+The addition of a control input allows the spacecraft to depart from the natural dynamics and intersect the section at another location denoted by the dashed circle.
 We use the cost function \( J \) to define a distance metric on the \Poincare section.
-Maximization of \( J \), or the minimization of \( -J \), along various directions on the \Poincare section allows us to generate the largest reachability set under the bounded control input.
+Maximization of \( J \), or the minimization of \( -J \), along various directions, which are parameterized using \( \phi_d \), on the \Poincare section allows us to generate the largest reachability set under the bounded control input.
 
@@
 where \( \vecbf{x}_n(t_f) \) is the final state of a control-free trajectory, while the term \( \vecbf{x}(t_f)\) is the final state of a trajectory under the influence of the control input.
-We use the matrix \( Q = \text{diag} \begin{pmatrix} 1 & 0 & 1 & 1 & 0 &1 \end{pmatrix} \in \R^{6 \times 6}\) to represent the mapping onto \( \Sigma \).
+We use the matrix \( Q = \text{diag} \begin{bmatrix} 1 & 0 & 1 & 1 & 0 &1 \end{bmatrix} \in \R^{6 \times 6}\) to represent the mapping onto \( \Sigma \).
 Maximization of the distance between \( \vecbf{x}_n \) and \(\vecbf{x} \), on the \Poincare section defined in~\cref{eq:poincare_section}, is equivalent to the minimization of \( J \) defined in~\cref{eq:cost}.
@@
 In addition, we use the terminal constraints to define a specific direction along which we seek to minimize the cost~\cref{eq:cost}.
-Since the \Poincare section is four-dimensiona, we parameterize a direction in \( \R^4 \)  using three angles \( \phi_1, \phi_2 , \phi_3 \).
-The terminal constraints are given as
+Since the \Poincare section is four-dimensional, we parameterize a direction in \( \R^4 \)  using three angles \( \phi_1, \phi_2 , \phi_3 \).
+The terminal constraints are given in terms of these angles as
 \begin{align}\label{eq:terminal_constraints}
@@
 \begin{align}\label{eq:optimal_control}
-    \vecbf{u} = - u_m \frac{\vecbf{\lambda}}{\norm{\vecbf{\lambda}}} .
+    \vecbf{u} = - u_m \frac{\vecbf{\lambda_{\vecbf{v}}}}{\norm{\vecbf{\lambda_{\vecbf{v}}}}} .
 \end{align}
@@
 Since the target periodic orbit also lies in the equatorial plane, we augment~\cref{eq:terminal_constraints} with an additional constraint \( m_5 = z = 0\) to ensure that the trajectories remain in the equatorial plane.
-Similarly, we also add another Lagrange multipler, \( \beta \in \R^{5 \times 1}\), to account for this addiitonal terminal constraint.
+Similarly, we also add another Lagrange multipler, \( \beta \in \R^{5 \times 1}\), to account for this additonal terminal constraint.
 The reachability set is computed by solving the two-point boundary value problem using a multiple shooting algorithm to satisfy the necessary conditions in~\cref{eq:necc_conditions}.
@@
 \Cref{fig:control} shows the control input required during the maneuver.
-The transfers show a large out of plane movement for a planar transfer
 We can see that the control constraint in~\cref{eq:control_constraint} is satisfied over the entire trajectory.
@@
 
-In this paper, an optimal transfer process, which combines the concepts of reachability and \Poincare section, is used to generate a transfer between periodic orbits about the asteroid 4769 Castalia.
+In this paper, an optimal transfer process, which combines the concepts of reachability sets on a \Poincare section, is used to generate a transfer between periodic orbits about the asteroid 4769 Castalia.
 We have linked several computations of the reachability set on a \Poincare section in order to design a transfer trajectory.

### 2016-08-15 manuscript.tex
Updated the plots with a new transfer
Corrected some typos

@@
 As a result, accurate numerical methods are required to determine optimal solutions.
-These methods are critically dependent on accurate initial guess in order to allow for convergence to an optimal solution.
+These methods are critically dependent on an accurate initial guess in order to allow for convergence to an optimal solution.
 
@@
 Finally,~\cref{eq:potential} is used to compute the gravitational potential on the spacecraft.
-The Laplacian, defined in~\cref{eq:laplacian}, gives a simple method to determine if the spacecraft has collided with the body~\cite{werner1996}
+The Laplacian, defined in~\cref{eq:laplacian}, gives a simple method to determine if the spacecraft has collided with the body~\cite{werner1996}.
 
@@
     \begin{bmatrix}
-        2.9786 \\ 0 \\ 0.0012 \\ 0\\ -0.0011 \\ 0
+        3.8161 \\ 0 \\ 0.0007 \\ 0\\ -0.0015 \\ 0
     \end{bmatrix} .
 \end{align}
-\Cref{fig:initial_transfer} shows the initial and desired periodic orbits which lie in the equatorial plane of Castalia.
+\Cref{fig:initial_transfer} shows the initial, \( \vecbf{x}_i \), and target, \( \vecbf{x}_t\), periodic orbits which lie in the equatorial plane of Castalia.
 Our goal is to transfer from a lower altitude to a higher altitude while remaining in the equatorial plane of the asteroid.
@@
 Since the target periodic orbit also lies in the equatorial plane, we augment~\cref{eq:terminal_constraints} with an additional constraint \( m_5 = z = 0\) to ensure that the trajectories remain in the equatorial plane.
-Similarly, we also add another Lagrange multipler, \( \beta \in \R^{5 \times 1}\), to account for this additonal terminal constraint.
+Similarly, we also add another Lagrange multipler, \( \beta \in \R^{5 \times 1}\), to account for this additional terminal constraint.
 The reachability set is computed by solving the two-point boundary value problem using a multiple shooting algorithm to satisfy the necessary conditions in~\cref{eq:necc_conditions}.
@@
 From~\cref{fig:poincare_xvsxdot}, we can see that the reachability set has grown in the \( \dot{x} \) dimension but has not been enlarged much in the \( x \) direction.
-Similarly,~\cref{fig:poincare_zvszdot} shows an increase in the \( \dot{z} \) component while still maintaining the \( z = 0 \) terminal constraint.
+Similarly,~\cref{fig:poincare_zvszdot} shows an increase in the \( \dot{z} \) component.
+There is a relatively large deviation of the \( z = 0 \) as seen by the trajectories in the second and third stages shown in~\cref{fig:poincare_zvszdot}. 
+This is primarily due to the competing constraints shown in~\cref{eq:terminal_constraints}.
+The shooting method must satisfy both a direction on the \Poincare section as well as the terminal constraint of \( z = 0\).
+For certain trajectories, this is more restrictive and results in a slightly larger terminal constraint violation.
 From the reachability set, we chose a trajectory and terminal state which minimizes a distance metric \( d(\vecbf{x}_f,\vecbf{x}_t) \) to the desired target

### 2016-08-16 manuscript.tex
Expanding detail in the introduction based on comments from Dr. Lee

@@
 
- \title{Low-Thrust Trajectory Design Near Asteroids Using Reachability Sets}
+ \title{Low-Thrust Trajectory Design Using Reachability Sets near Asteroid 4769 Castalia}
 
@@
     \thanks{Doctoral Student, \href{mailto:skulumani@gwu.edu}{skulumani@gwu.edu}. Student AIAA Member.}
-  \ and Taeyoung Lee\thanksibid{2}\thanks{Associate Professor, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}. AIAA Member.}\\
+  \ and Taeyoung Lee\thanksibid{2}\thanks{Associate Professor, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}.}\\
   {\normalsize\itshape
@@
 
-% Must estimate gravity and shape from ground based optical measurements
 % most use a spherical harmonic model or a ellipsoid model but we use a polyhedron model
@@
 Radio tracking data of an orbiting spacecraft allows one to estimate the series coefficients.
-The harmonic representation is guaranteed to converge outside of the circumscribing sphere and can be truncated at a finite order based on accuracy requirements.
+The harmonic representation is guaranteed to converge outside of the circumscribing sphere and can be truncated at a finite order based on accuracy requirements~\cite{scheeres2012a}.
 However, the harmonic expansion is always an approximation as a result of the infinite order series used in the representation.
 Additionally, the harmonic model used outside of the circumscribing sphere is not guaranteed to converge inside the sphere.
-As a result, additional steps must be taken to determine a valid harmonic expansion for particles close to the body.
-This results in a cumbersome gravity field model that requires additional constraints to ensure continuity and validity at the radius of the circumscribing sphere~\cite{werner1994 ,werner1996}.
-Instead, we model the asteroid as a constant-density polyhedron and avoid the issues of the harmonic expansion.
+
+A popular approach to deal with this divergence is to use a different gravitational model within the circumscribing sphere.
+For example, Reference~\citenum{scheeres2000} uses both a polyhedron field and a spherical harmonic expansion to represent the full gravitational field of the body.
+The spherical harmonic coefficients are computed from the polyhedron shape model using a constant density assumption~\cite{werner1997}.
+This model is applied while close to the body while the harmonic expansion is applied when outside the circumscribing sphere.
+Similarly, Reference~\citenum{herrera2014} uses two different harmonic expansion models to represent the gravitational field inside and outside of the circumscribing sphere.
+In this case, the coefficients must be carefully chosen to ensure continuity of the gravitational field at the circumscribing sphere.
+In both cases, this type of model results in a cumbersome gravity field expression that requires additional constraints to ensure continuity and validity at the radius of the circumscribing sphere.
+Any integration software will need to incorporate a switching mechanism between the models when crossing the circumscribing sphere.
+Instead, we use a different approach and model the asteroid as a constant-density polyhedron.
+
+In contrast, the polyhedron model results in an exact closed form expression of the gravitational potential field~\cite{werner1994,werner1996}.
+This type of model results in the exact potential up to the accuracy of the shape model and a constant density assumption.
+However, the calculation of the potential, or the acceleration, requires a summation over every face of the polyhedron. 
+As a result, it typically requires a large amount of computation in contrast to the harmonic expansion models. 
+However, the formulation is well suited to parallelization and improvements with efficient coding practices. 
+Finally, the polyhedron method is well suited to trajectories passing close to the body and offers a simple metric to determine if a particle is inside the asteroid.
+The use of the polyhedron model results in a single expression of the gravitational field that is valid everywhere around the body of the asteroid.
 
@@
 
-% similarity to the three body problem
+% Discuss previous work and their drawbacks to determine transfers about asteroids
+
+% Detail of work - more empasis and add the novelty of our work
 The irregular shape of asteroids leads to a richer dynamics as compared to the familiar Kepler's problem.
@@
 Therefore, the spherical harmonic representation is not ideal for landing trajectories or those passing close to the surface.
-
-In contrast, the polyhedron model results in an exact closed form expression of the gravitational potential field~\cite{werner1994}.
-In addition, the model results in the exact potential for the given shape
-However, the calculation of the potential, or the acceleration, requires a summation over every face of the polyhedron. 
-As a result, it typically requires a large amount of computation in contrast to the harmonic expansion. 
-However, the formulation is well suited to parallelization and improvements with efficient coding practices. 
-Finally, the polyhedron method is well suited to trajectories passing close to the body and offers a simple metric to determine if a particle is inside the asteroid.
 
@@
     \begin{bmatrix}
-        3.8161 \\ 0 \\ 0.0007 \\ 0\\ -0.0015 \\ 0
+        6.1175 \\ 0 \\ 0.0001 \\ 0\\ -0.0025 \\ 0
     \end{bmatrix} .

### 2016-08-16 manuscript.tex
Add corrections suggested by Dr. Lee

@@
 While there has been significant study of interplanetary transfer trajectories, relatively less analysis has been conducted on operations in the vicinity of asteroids.
-The dynamic environment around asteroids is strongly perturbed and challenging for analysis and mission operation.
+The dynamic environment around asteroids is strongly perturbed and challenging for analysis and mission operation~\cite{scheeres1994,scheeres2000}.
 Due to their low mass, which results in a low gravitational attraction, asteroids may have irregular shapes and potentially chaotic spin states.
@@
 % Discuss previous work and their drawbacks to determine transfers about asteroids
+There has been a large amount of work on the optimal control of spacecraft orbital transfers in the three-body problem~\cite{mingotti2011,grebow2011}.
+The dynamics of a spacecraft about small bodies is very similar to that of the three-body problem and much of the theory developed there is also applicable.
+Typically, the optimal control problem is solved via direct methods, which approximate the continuous time problem as a parameter optimization problem.
+The state and control trajectories are discretly parameterized and solved in the form of a nonlinear optimization problem.
+Alternatively, indirect methods apply calculus of variations to derive the necessary conditions for optimality. 
+This yields a lower dimensioned problem as compared to the direct approach.
+In addition, satisfication of the necessary conditions guarantee local optimality in contrast to directo methods which result in sub-optimal solutions.
 
@@
 The irregular shape of asteroids leads to a richer dynamics as compared to the familiar Kepler's problem.
-The motion of particles around asteroids is modeled using the restricted full two-body problem.
+We model the motion of particles around asteroids using the restricted full two-body problem.
 This model has many similarities with the restricted three body problem, and much of the theory developed for the three-body problem is also applicable~\cite{mondelo2010,herrera2014}.
-In this paper, we extend the design method developed in the three-body problem to motion about asteroids~\cite{kulumani2015}.
-Our approach avoids the difficulties in selecting an appropriate initial guess for optimization.
+
+In this paper, we extend the design method previously developed in the three-body problem to motion about asteroids~\cite{kulumani2015}.
+Our systematic approach avoids the difficulties in selecting an appropriate initial guess for optimization.
 We instead utilize the concept of the reachability set to enable a simple methodology of selecting initial conditions to achieve general orbital transfers.
+This method allows the spacecraft to depart from fixed periodic solutions through the use of a low-thrust propulsion system.
+In addition, we utilize a polyhedron gravitational model which is accurate and is globally applicable about the asteroid.
+
+We formulate an optimal control problem to calculate the reachability set on a lower dimensional \Poincare section.
 Given an initial condition and fixed time horizon, the reachable set is the set of states attainable, subject to the operational constraints of the spacecraft.
-We calculate the reachable set on a lower dimensional \Poincare section. 
 The generation of the reachable set allows for a more systematic method of determining initial conditions and eases the burden on the designer.
+The \Poincare section reduces the dimensionality of teh system dynamics to the study of a related discrete update map.
+This allows for the design of complex transfer trajectories through the use of a lower dimensional space.
+Rather than relying on intuition or insight into the problem, trajectory states are chosen which minimize a distance metric toward a desired target on the \Poincare section.
 This simple methodology allows for extended transfer trajectories which iteratively approach a desired target orbit.
+
+In short, the authors present a systematic method of generating optimal transfer orbits about asteroids.
+Typically, optimal transfers are generated using a direct optimization method which results in a sub-optimal solution.
+This paper present an indirect optimal control formulation to generate the reachability set on a \Poincare section.
+Using the reachability set on the \Poincare section allows for a simple method of choosing trajectories which approach a target.
+This method allows us to avoid the difficulties inherent in choosing valid initial conditions for the computation of optimal transfer trajectories.
+We develop the optimal control formulation and apply this method to a transfer about asteroid 4769 Castalia.
 
@@
 
-Consider three vectors \( \vecbf{v}_1, \vecbf{v}_2, \vecbf{v}_3 \), assumed to be ordered in a counterclockwise direction, which define a face.
+Consider three vectors \( \vecbf{v}_1, \vecbf{v}_2, \vecbf{v}_3 \in \R^{3 \times 1} \), assumed to be ordered in a counterclockwise direction, which define a face.
 It is easy to define the three edges of each face as
 \begin{align}\label{eq:edges}
-    \vecbf{e}_{i+1,i} = \vecbf{v}_{i+1} - \vecbf{v}_i ,
+    \vecbf{e}_{i+1,i} = \vecbf{v}_{i+1} - \vecbf{v}_i \in \R^{3 \times 1 },
 \end{align}
@@
 \begin{align}\label{eq:face_normal}
-    \hat{\vecbf{n}}_f &= \parenth{\vecbf{v}_{2} - \vecbf{v}_1} \times \parenth{\vecbf{v}_{3} - \vecbf{v}_2} ,
+    \hat{\vecbf{n}}_f &= \parenth{\vecbf{v}_{2} - \vecbf{v}_1} \times \parenth{\vecbf{v}_{3} - \vecbf{v}_2} \in \R^{3 \times 1},
 \end{align}
@@
 \begin{align}\label{eq:face_dyad}
-    \vecbf{F}_f &= \hat{\vecbf{n}}_f \hat{\vecbf{n}}_f .
+    \vecbf{F}_f &= \hat{\vecbf{n}}_f \hat{\vecbf{n}}_f \in \R^{3 \times 3}.
 \end{align}
@@
 \begin{align}\label{eq:edge_dyad}
-    \vecbf{E}_{12} = \hat{\vecbf{n}}_A \hat{\vecbf{n}}_{12}^A + \hat{\vecbf{n}}_B \hat{\vecbf{n}}_{21}^B .
+    \vecbf{E}_{12} = \hat{\vecbf{n}}_A \parenth{\hat{\vecbf{n}}_{12}^A}^T + \hat{\vecbf{n}}_B \hat{\vecbf{n}}_{21}^B \in \R^{3 \times 3}.
 \end{align}
-The edge dyad, \( \vecbf{E}_e \), is defined for each edge and is a function of the two adjacent faces meeting at the edge.
-The face dyad, \( \vecbf{F}_f \), is defined for each face and is a function of the face normal vectors.
+The edge dyad \( \vecbf{E}_e  \), is defined for each edge and is a function of the two adjacent faces meeting at that edge.
+The face dyad \( \vecbf{F}_f \), is defined for each face and is a function of the face normal vectors.
 
-Let \( \vecbf{r}_i \) be the vector from the spacecraft to the vertex \( \vecbf{v}_i \) and it's length is given by \( r_i = \norm{\vecbf{r}_i} \).
-The per-edge factor \( L_e \), for the edge connecting vertices \( \vecbf{v}_i \) and \( \vecbf{v}_j \), with a constant length \( e_{ij} \) is
+Let \( \vecbf{r}_i \in \R^{3 \times 1} \) be the vector from the spacecraft to the vertex \( \vecbf{v}_i \) and it's length is given by \( r_i = \norm{\vecbf{r}_i} \in \R^{1} \).
+The per-edge factor \( L_e \in \R^{1}\), for the edge connecting vertices \( \vecbf{v}_i \) and \( \vecbf{v}_j \), with a constant length \( e_{ij} \) is
 \begin{align}\label{eq:edge_factor}
@@
 \end{align}
-For the face defined by the vertices \( \vecbf{v}_i, \vecbf{v}_j, \vecbf{v}_k \) the per-face factor \( \omega_f \) is
+For the face defined by the vertices \( \vecbf{v}_i, \vecbf{v}_j, \vecbf{v}_k \) the per-face factor \( \omega_f \in \R^{1} \) is
 \begin{align}\label{eq:face_factor}
@@
 \begin{align}\label{eq:potential}
-    U(\vecbf{r}) &= 1\frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f ,
+    U(\vecbf{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f ,
 \end{align}
@@
 \begin{align}\label{eq:body_eoms}
-    \ddot{\vecbf{r}} + 2 \vecbf{\Omega} \times \dot{\vecbf{r}} + \vecbf{\Omega} \times \parenth{ \vecbf{\Omega} \times \vecbf{r} } + \dot{\vecbf{\Omega}} \times \vecbf{r} = U_{\vecbf{r}} ,
+    \ddot{\vecbf{r}} + 2 \vecbf{\Omega} \times \dot{\vecbf{r}} + \vecbf{\Omega} \times \parenth{ \vecbf{\Omega} \times \vecbf{r} } + \dot{\vecbf{\Omega}} \times \vecbf{r} = \nabla U(\vecbf{r}) ,
 \end{align}
@@
 
-In this situation, the state is defined as \( \vecbf{x} = \begin{bmatrix}\vecbf{r} &\vecbf{v} \end{bmatrix}^T\) with \(\vecbf{r} = \begin{bmatrix} x & y & z \end{bmatrix}^T \in \R^{3\times1}\) and \(\vecbf{v}= \begin{bmatrix} \dot{x} & \dot{y} & \dot{z} \end{bmatrix}^T \in \R^{3\times1}\) representing the position and velocity with respect to the body-fixed frame, respectively.
-We further assume that our spacecraft is capable of exerting a translational acceleration, \( \vecbf{u} \in \R^{3\times1} \), in any direction, while subject to a maximum magnitude constraint.
+In this situation, the state is defined as \( \vecbf{x} = \bracket{\vecbf{r}~\>\vecbf{v}}^T\) with \(\vecbf{r} = \bracket{x~\>y~\>z}^T \in \R^{3\times1}\) and \(\vecbf{v}= \bracket{ \dot{x}~\>\dot{y}~\>\dot{z} }^T \in \R^{3\times1}\) representing the position and velocity with respect to the body-fixed frame, respectively.
+We further assume that our spacecraft is capable of exerting a translational acceleration, \( \vecbf{u} \in \R^{3\times1} \), in any direction, while subject to a maximum magnitude constraint, \( \norm{\vecbf{u}} \leq u_m \).
 This is typical of many spacecraft which offer full rotational freedom and can direct a potentially varying force or acceleration in any direction.
@@
 where \( \vecbf{x}_n(t_f) \) is the final state of a control-free trajectory, while the term \( \vecbf{x}(t_f)\) is the final state of a trajectory under the influence of the control input.
-We use the matrix \( Q = \text{diag} \begin{bmatrix} 1 & 0 & 1 & 1 & 0 &1 \end{bmatrix} \in \R^{6 \times 6}\) to represent the mapping onto \( \Sigma \).
+We use the matrix \( Q = \text{diag} \bracket{1~\>0~\> 1~\> 1~\>0~\>1 } \in \R^{6 \times 6}\) to represent the mapping onto \( \Sigma \).
 Maximization of the distance between \( \vecbf{x}_n \) and \(\vecbf{x} \), on the \Poincare section defined in~\cref{eq:poincare_section}, is equivalent to the minimization of \( J \) defined in~\cref{eq:cost}.
@@
 \end{align}
+We select the terminal time, \( t_f \), from the time required for the uncontrolled trajectory to return back to the \Poincare section.
 The constraint \( m_1 = 0 \) ensures that the terminal state lies on the \Poincare section.
@@
 \end{align}
-The costate is given by \( \vecbf{\lambda} = \begin{bmatrix} \vecbf{\lambda}_r & \vecbf{\lambda}_v \end{bmatrix}^T \in \R^{6 \times 1}\), \( \vecbf{\beta} \in \R^{4 \times 1} \) are the additional Lagrange multiplers associated with the terminal constraints in~\cref{eq:terminal_constraints}, and \( \mu \) is a Lagrange multipler associated with the control constraint in~\cref{eq:control_constraint}.
+The costate is given by \( \vecbf{\lambda} = \bracket{ \vecbf{\lambda}_r~\> \vecbf{\lambda}_v }^T \in \R^{6 \times 1}\), \( \vecbf{\beta} \in \R^{4 \times 1} \) are the additional Lagrange multiplers associated with the terminal constraints in~\cref{eq:terminal_constraints}, and \( \mu \) is a Lagrange multipler associated with the control constraint in~\cref{eq:control_constraint}.
 
@@
 In this transfer example we also have used a reduced model of Castalia.
-Rather than using the full \num{4092} face model we reduce the number of faces to \num{1024}. 
+Rather than using the full \num{4092} face model we reduce the number of faces to \num{1024} using the Matlab function \verb+reducepatch+. 
 This greatly speeds up the computation with only a small difference in the gravitational field.
@@
 We first compute the reachability set originating from the initial periodic orbit at \( \vecbf{x}_i\) for a fixed time of flight and bounded control magnitude as defined previously.
-Since the target periodic orbit also lies in the equatorial plane, we augment~\cref{eq:terminal_constraints} with an additional constraint \( m_5 = z = 0\) to ensure that the trajectories remain in the equatorial plane.
-Similarly, we also add another Lagrange multipler, \( \beta \in \R^{5 \times 1}\), to account for this additional terminal constraint.
 The reachability set is computed by solving the two-point boundary value problem using a multiple shooting algorithm to satisfy the necessary conditions in~\cref{eq:necc_conditions}.
@@
 This results in a total of \(10^3\) trajectories which approximate the reachability set on the \Poincare section.
+
 We visualize the section using the two figures in~\cref{fig:poincare_section}.
@@
 Similarly,~\cref{fig:poincare_zvszdot} shows an increase in the \( \dot{z} \) component.
-There is a relatively large deviation of the \( z = 0 \) as seen by the trajectories in the second and third stages shown in~\cref{fig:poincare_zvszdot}. 
-This is primarily due to the competing constraints shown in~\cref{eq:terminal_constraints}.
-The shooting method must satisfy both a direction on the \Poincare section as well as the terminal constraint of \( z = 0\).
-For certain trajectories, this is more restrictive and results in a slightly larger terminal constraint violation.
 From the reachability set, we chose a trajectory and terminal state which minimizes a distance metric \( d(\vecbf{x}_f,\vecbf{x}_t) \) to the desired target
@@
 The trajectory which minimizes \( d \) is indicated by the red marker in~\cref{fig:poincare_section,fig:phi_distance}.
-Since the reachability set does not include the target we use the minimum state from the first stage to initialize another reachability computation.
+Since the first reachability set does not include the target we use the minimum state from the first stage to initialize another reachability computation.
 Once again we compute the reachability set by discretization of the angles \( \phi_i \) on the \Poincare section.
-This second stage, represented by the blue markers in~\cref{fig:poincare_section,fig:phi_distance}, further increase the \( x \) component but does not reach the target orbit.
-As a result, a third stage is generated in a similar manner and shown by the green markers in~\cref{fig:poincare_section,fig:phi_distance}.
-We can see in~\cref{fig:poincare_section} that the reachability set of the third stage includes both the \( x \) and \( z\) components of the target periodic orbit.
-At the same time there is a relatively large difference between the \( \dot{x} \) and \( \dot{z} \) components of the third stage and the target orbit.
-In practice this is not a large concern as we have direct control over the spacecraft velocity via the control input.
+This second stage, represented by the cyan markers in~\cref{fig:poincare_section,fig:phi_distance}, further increases the \( x, z\) components but does not reach the target orbit.
+As a result, a third and forth stage are generated in a similar manner and shown by the green and blue markers in~\cref{fig:poincare_section,fig:phi_distance}, respectively.
+We can see in~\cref{fig:poincare_section} that the reachability set of the forth stage includes both the \( x \) and \( z\) components of the target periodic orbit.
+At the same time there is a relatively large difference between the \( \dot{x} \), \( \dot{z} \), and \( z \) components of the forth stage and the target orbit.
+In practice this is not a large concern as we have direct control over the spacecraft velocity via the control input and the equatorial plane still remains within the reachability set of the transfer.
 

### 2016-08-17 manuscript.tex
Correct some errors in the paper

@@
 In this case, the coefficients must be carefully chosen to ensure continuity of the gravitational field at the circumscribing sphere.
-In both cases, this type of model results in a cumbersome gravity field expression that requires additional constraints to ensure continuity and validity at the radius of the circumscribing sphere.
+In both cases, this type of approach results in a cumbersome gravity field expression that requires additional constraints to ensure continuity and validity at the radius of the circumscribing sphere.
 Any integration software will need to incorporate a switching mechanism between the models when crossing the circumscribing sphere.
@@
 
-In contrast, the polyhedron model results in an exact closed form expression of the gravitational potential field~\cite{werner1994,werner1996}.
+The polyhedron model results in an exact closed form expression of the gravitational potential field~\cite{werner1994,werner1996}.
 This type of model results in the exact potential up to the accuracy of the shape model and a constant density assumption.
@@
 Finally, the polyhedron method is well suited to trajectories passing close to the body and offers a simple metric to determine if a particle is inside the asteroid.
-The use of the polyhedron model results in a single expression of the gravitational field that is valid everywhere around the body of the asteroid.
+The use of the polyhedron model results in a single expression of the gravitational field that is valid everywhere around the body.
 
@@
 As a result, accurate numerical methods are required to determine optimal solutions.
-These methods are critically dependent on an accurate initial guess in order to allow for convergence to an optimal solution.
+These methods are critically dependent on an accurate initial guess in order to allow for convergence.
 
 % Discuss previous work and their drawbacks to determine transfers about asteroids
-There has been a large amount of work on the optimal control of spacecraft orbital transfers in the three-body problem~\cite{mingotti2011,grebow2011}.
-The dynamics of a spacecraft about small bodies is very similar to that of the three-body problem and much of the theory developed there is also applicable.
+We model the motion of particles around asteroids using the restricted full two-body problem.
+The dynamics of a spacecraft about small bodies is very similar to that of the three-body problem.
+This model has many similarities with the restricted three body problem, and much of the theory developed for the three-body problem is also applicable~\cite{mondelo2010,herrera2014}.
+In addition, there has been a large amount of work on the optimal control of spacecraft orbital transfers in the three-body problem~\cite{mingotti2011,grebow2011}.
 Typically, the optimal control problem is solved via direct methods, which approximate the continuous time problem as a parameter optimization problem.
@@
 In addition, satisfication of the necessary conditions guarantee local optimality in contrast to directo methods which result in sub-optimal solutions.
-
-% Detail of work - more empasis and add the novelty of our work
-The irregular shape of asteroids leads to a richer dynamics as compared to the familiar Kepler's problem.
-We model the motion of particles around asteroids using the restricted full two-body problem.
-This model has many similarities with the restricted three body problem, and much of the theory developed for the three-body problem is also applicable~\cite{mondelo2010,herrera2014}.
 
@@
 The generation of the reachable set allows for a more systematic method of determining initial conditions and eases the burden on the designer.
-The \Poincare section reduces the dimensionality of teh system dynamics to the study of a related discrete update map.
-This allows for the design of complex transfer trajectories through the use of a lower dimensional space.
-Rather than relying on intuition or insight into the problem, trajectory states are chosen which minimize a distance metric toward a desired target on the \Poincare section.
+The \Poincare section reduces the dimensionality of the system dynamics to the study of a related discrete update map.
+This allows for the design of complex transfer trajectories on a lower dimensional space.
+Rather than relying on intuition or insight into the problem, trajectories are chosen which minimize a distance metric toward a desired target on the \Poincare section.
 This simple methodology allows for extended transfer trajectories which iteratively approach a desired target orbit.
@@
 Using the reachability set on the \Poincare section allows for a simple method of choosing trajectories which approach a target.
+In addition, the reachability set gives an indication of the regions of the phase space accessible to the spacecraft.
 This method allows us to avoid the difficulties inherent in choosing valid initial conditions for the computation of optimal transfer trajectories.
@@
 \begin{align}\label{eq:edge_normal}
-    \hat{\vecbf{n}}_{i+1,i}^f &= \parenth{\vecbf{v}_{i+1} - \vecbf{v}_i} \times \hat{\vecbf{n}}_f .
+    \hat{\vecbf{n}}_{i+1,i}^f &= \parenth{\vecbf{v}_{i+1} - \vecbf{v}_i} \times \hat{\vecbf{n}}_f \in \R^{3 \times 1}.
 \end{align}
@@
 \begin{align}\label{eq:edge_dyad}
-    \vecbf{E}_{12} = \hat{\vecbf{n}}_A \parenth{\hat{\vecbf{n}}_{12}^A}^T + \hat{\vecbf{n}}_B \hat{\vecbf{n}}_{21}^B \in \R^{3 \times 3}.
+    \vecbf{E}_{12} = \hat{\vecbf{n}}_A \hat{\vecbf{n}}_{12}^A + \hat{\vecbf{n}}_B \hat{\vecbf{n}}_{21}^B \in \R^{3 \times 3}.
 \end{align}
@@
 Let \( \vecbf{r}_i \in \R^{3 \times 1} \) be the vector from the spacecraft to the vertex \( \vecbf{v}_i \) and it's length is given by \( r_i = \norm{\vecbf{r}_i} \in \R^{1} \).
-The per-edge factor \( L_e \in \R^{1}\), for the edge connecting vertices \( \vecbf{v}_i \) and \( \vecbf{v}_j \), with a constant length \( e_{ij} \) is
+The per-edge factor \( L_e \in \R^{1}\), for the edge connecting vertices \( \vecbf{v}_i \) and \( \vecbf{v}_j \), with a constant length \( e_{ij} = \norm{\vecbf{e}_{ij}} \in \R^1\) is
 \begin{align}\label{eq:edge_factor}
@@
 \begin{align}\label{eq:potential}
-    U(\vecbf{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f ,
+    U(\vecbf{r}) &= \frac{1}{2} G \sigma \sum_{e \in \text{edges}} \vecbf{r}_e \cdot \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e - \frac{1}{2}G \sigma \sum_{f \in \text{faces}} \vecbf{r}_f \cdot \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f \in \R^1,
 \end{align}
@@
 \begin{align}
-    \nabla U ( \vecbf{r} ) &= -G \sigma \sum_{e \in \text{edges}} \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e + G \sigma \sum_{f \in \text{faces}} \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f , \label{eq:attraction}\\
-    \nabla \nabla U ( \vecbf{r} ) &= G \sigma \sum_{e \in \text{edges}} \vecbf{E}_e  \cdot L_e - G \sigma \sum_{f \in \text{faces}} \vecbf{F}_f \cdot \omega_f , \label{eq:gradient_matrix}\\
-    \nabla^2 U &= -G \sigma \sum_{f \in \text{faces}}  \omega_f \label{eq:laplacian}.
+    \nabla U ( \vecbf{r} ) &= -G \sigma \sum_{e \in \text{edges}} \vecbf{E}_e \cdot \vecbf{r}_e \cdot L_e + G \sigma \sum_{f \in \text{faces}} \vecbf{F}_f \cdot \vecbf{r}_f \cdot \omega_f \in \R^{3 \times 1} , \label{eq:attraction}\\
+    \nabla \nabla U ( \vecbf{r} ) &= G \sigma \sum_{e \in \text{edges}} \vecbf{E}_e  \cdot L_e - G \sigma \sum_{f \in \text{faces}} \vecbf{F}_f \cdot \omega_f \in \R^{3 \times 3}, \label{eq:gradient_matrix}\\
+    \nabla^2 U &= -G \sigma \sum_{f \in \text{faces}}  \omega_f \in \R^1 .\label{eq:laplacian}
 \end{align}
@@
 \end{align}
-where \( \vecbf{\Omega} \) is the instantaneous angular velocity vector of the asteroid represented in the body-fixed frame, \( \vecbf{r} \) is the position of the particle in the body-fixed frame, and \( U_{\vecbf{r}} \) is the gradient of the gravitational potential~\cite{scheeres2012a}.
-We assume that the asteroid rotates at a uniform rate, \( \norm{\vecbf{\Omega}} = \omega \), about the axis of the maximum moment of inertia, \( \vecbf{\Omega} = \omega \hat{\vecbf{z} }\).
+where \( \vecbf{\Omega} \in \R^{3 \times 1}\) is the instantaneous angular velocity vector of the asteroid represented in the body-fixed frame, \( \vecbf{r} \) is the position of the particle in the body-fixed frame, and \( \nabla U_{\vecbf{r}} \) is the gradient of the gravitational potential~\cite{scheeres2012a}.
+We assume that the asteroid rotates at a uniform rate, \( \norm{\vecbf{\Omega}} = \omega \in \R^1 \), about the axis of the maximum moment of inertia, \( \vecbf{\Omega} = \omega \hat{\vecbf{z} }\).
 As a result, we can represent the equations of motion in scalar form as
@@
 
-In this situation, the state is defined as \( \vecbf{x} = \bracket{\vecbf{r}~\>\vecbf{v}}^T\) with \(\vecbf{r} = \bracket{x~\>y~\>z}^T \in \R^{3\times1}\) and \(\vecbf{v}= \bracket{ \dot{x}~\>\dot{y}~\>\dot{z} }^T \in \R^{3\times1}\) representing the position and velocity with respect to the body-fixed frame, respectively.
+In this situation, the state is defined as \( \vecbf{x} = \bracket{\vecbf{r}~\>\vecbf{v}}^T \in \R^{6 \times 1}\) with \(\vecbf{r} = \bracket{x~\>y~\>z}^T \in \R^{3\times1}\) and \(\vecbf{v}= \bracket{ \dot{x}~\>\dot{y}~\>\dot{z} }^T \in \R^{3\times1}\) representing the position and velocity with respect to the body-fixed frame, respectively.
 We further assume that our spacecraft is capable of exerting a translational acceleration, \( \vecbf{u} \in \R^{3\times1} \), in any direction, while subject to a maximum magnitude constraint, \( \norm{\vecbf{u}} \leq u_m \).
@@
 such that we parameterize all directions on the three sphere, \(\S^3\).
-Finally, we also incorporate a control acceleration magnitude constraint given by
+Finally, we also incorporate the control acceleration magnitude constraint as
 \begin{align}\label{eq:control_constraint}
@@
 A final optimal transfer is computed to satisfy the fixed terminal state \( \vecbf{x}(t_f) = \vecbf{x}_t \) and the bounded control magnitude constraint.
-\Cref{fig:trajectory} shows the entire transfer trajectory, from the three reachable set trajectories as well as the final transfer to the target.
+\Cref{fig:trajectory} shows the entire transfer trajectory, from the four reachable set trajectories as well as the final transfer to the target.
 \begin{figure}[htbp] 

### 2016-08-17 manuscript.tex
Some more corrections from Dr. Lee and added acknowledgement section

@@
 
-We present a computational approach for the design of continuous low thrust transfers around asteroids.
+We present a computational approach for the design of continuous low thrust transfers around an asteroid.
 These transfers are computed through the use of a reachability set generated on a lower dimensional \Poincare surface.
@@
 The spherical harmonic coefficients are computed from the polyhedron shape model using a constant density assumption~\cite{werner1997}.
-This model is applied while close to the body while the harmonic expansion is applied when outside the circumscribing sphere.
+This model is applied close to the body while the harmonic expansion is applied when outside the circumscribing sphere.
 Similarly, Reference~\citenum{herrera2014} uses two different harmonic expansion models to represent the gravitational field inside and outside of the circumscribing sphere.
@@
 \end{align}
-where \( \vecbf{\Omega} \in \R^{3 \times 1}\) is the instantaneous angular velocity vector of the asteroid represented in the body-fixed frame, \( \vecbf{r} \) is the position of the particle in the body-fixed frame, and \( \nabla U_{\vecbf{r}} \) is the gradient of the gravitational potential~\cite{scheeres2012a}.
+where \( \vecbf{\Omega} \in \R^{3 \times 1}\) is the instantaneous angular velocity vector of the asteroid represented in the body-fixed frame, \( \vecbf{r} \) is the position of the particle in the body-fixed frame, and \( \nabla U(\vecbf{r}) \) is the gradient of the gravitational potential~\cite{scheeres2012a}.
 We assume that the asteroid rotates at a uniform rate, \( \norm{\vecbf{\Omega}} = \omega \in \R^1 \), about the axis of the maximum moment of inertia, \( \vecbf{\Omega} = \omega \hat{\vecbf{z} }\).
@@
 \end{align}
-The costate is given by \( \vecbf{\lambda} = \bracket{ \vecbf{\lambda}_r~\> \vecbf{\lambda}_v }^T \in \R^{6 \times 1}\), \( \vecbf{\beta} \in \R^{4 \times 1} \) are the additional Lagrange multiplers associated with the terminal constraints in~\cref{eq:terminal_constraints}, and \( \mu \) is a Lagrange multipler associated with the control constraint in~\cref{eq:control_constraint}.
+The costate is given by \( \vecbf{\lambda} = \bracket{ \vecbf{\lambda}_r~\> \vecbf{\lambda}_v }^T \in \R^{6 \times 1}\). 
+The vector \( \vecbf{\beta} \in \R^{4 \times 1} \) are the additional Lagrange multiplers associated with the terminal constraints in~\cref{eq:terminal_constraints}, and \( \mu \) is a Lagrange multipler associated with the control constraint in~\cref{eq:control_constraint}.
 
@@
 \begin{align}\label{sec:interior_constraints}
-    \vecbf{x}_{m-1}^{-} &= \vecbf{x}_m^{+} , \\
-    \vecbf{\lambda}_{m-1}^{-} &= \vecbf{\lambda}_m^{+},
+    \begin{split}
+        \vecbf{x}(t_{m-1}^{-}) &= \vecbf{x}(t_{m}^{+}) , \\
+        \vecbf{\lambda}(t_{m-1}^{-}) &= \vecbf{\lambda}(t_{m}^{+}),        
+    \end{split}
 \end{align}
@@
 
+\section*{Acknowledgments}\label{sec:acknowledgments}
+
+This research has been supported in part by NSF under the grants CMMI-1243000, CMMI-1335008, and CNS-1337722.
+
 \bibliographystyle{aiaa}

### 2016-08-18 manuscript.tex
Add some more corrections and comments from Dr. Lee

@@
 This yields a lower dimensioned problem as compared to the direct approach.
-In addition, satisfication of the necessary conditions guarantee local optimality in contrast to directo methods which result in sub-optimal solutions.
+In addition, satisfication of the necessary conditions guarantee local optimality in contrast to direct methods which result in sub-optimal solutions.
 
@@
 We represent the gravitational potential of the asteroid using a polyhedron gravitation model.
-This model is composed of a polyhedron, a three-dimensional solid body, that is defined by a series of vectors in the body-fixed frame.
+This model is composed of a polyhedron, which is a three-dimensional solid body, that is defined by a series of vectors in the body-fixed frame.
 The vectors define vertices in the body-fixed frame as well as planar faces which compose the surface of the asteroid.
@@
 where \( \vecbf{\Omega} \in \R^{3 \times 1}\) is the instantaneous angular velocity vector of the asteroid represented in the body-fixed frame, \( \vecbf{r} \) is the position of the particle in the body-fixed frame, and \( \nabla U(\vecbf{r}) \) is the gradient of the gravitational potential~\cite{scheeres2012a}.
-We assume that the asteroid rotates at a uniform rate, \( \norm{\vecbf{\Omega}} = \omega \in \R^1 \), about the axis of the maximum moment of inertia, \( \vecbf{\Omega} = \omega \hat{\vecbf{z} }\).
+We assume that the asteroid rotates at a uniform rate, \( \norm{\vecbf{\Omega}} = \omega \in \R^1 \), about the axis of the maximum moment of inertia, i.e.\ \( \vecbf{\Omega} = \omega \hat{\vecbf{z} }\).
 As a result, we can represent the equations of motion in scalar form as
@@
 
-\section{Reachability Set on \Poincare Section}\label{sec:reachability}
+\section{Reachability Set on a \Poincare Section}\label{sec:reachability}
 

### 2016-09-21 manuscript.tex
Remove path to figures for arxiv
Correct some typos

@@
   Shankar Kulumani\thanksibid{1}%
-    \thanks{Doctoral Student, \href{mailto:skulumani@gwu.edu}{skulumani@gwu.edu}. Student AIAA Member.}
+    \thanks{Doctoral Student, \href{mailto:skulumani@gwu.edu}{skulumani@gwu.edu}. Student Member AIAA.}
   \ and Taeyoung Lee\thanksibid{2}\thanks{Associate Professor, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}.}\\
@@
 This insight offers additional detail into the formation of the Earth and also the probable formation of other planetary bodies.
-Of particular interest are those near-Earth asteroids (NEA) which inhabit heliocentric orbits in vicinity of the Earth.
+Of particular interest are those near-Earth asteroids (NEA) which inhabit heliocentric orbits in the vicinity of the Earth.
 These easily accessible bodies provide attractive targets to support space industrialization, mining operations, and scientific missions.
@@
 Any integration software will need to incorporate a switching mechanism between the models when crossing the circumscribing sphere.
-Instead, we use a different approach and model the asteroid as a constant-density polyhedron.
+Instead, we use a simpler approach and model the asteroid as a constant-density polyhedron.
 
@@
 This method allows the spacecraft to depart from fixed periodic solutions through the use of a low-thrust propulsion system.
-In addition, we utilize a polyhedron gravitational model which is accurate and is globally applicable about the asteroid.
+In addition, we utilize a polyhedron gravitational model which is accurate and globally applicable about the asteroid.
 
@@
 This method allows us to avoid the difficulties inherent in choosing valid initial conditions for the computation of optimal transfer trajectories.
-We develop the optimal control formulation and apply this method to a transfer about asteroid 4769 Castalia.
+We develop the optimal control formulation and apply this method to an example transfer about asteroid 4769 Castalia.
 
@@
 
-In this analysis we consider transfers about the asteroid 4769 Castalia.
+In this analysis, we consider transfers about the asteroid 4769 Castalia.
 Castalia has an accurate shape model and is also considered a potentially hazardous asteroid with a possibility of Earth impact~\cite{hudson1994}.
 We model the gravitational potential field of Castalia using a polyhedron gravity model instead of using a spherical harmonic expansion.
-The spherical harmonic expansion is a popular method of representing the gravity field~\cite{scheeres1996}.
-Approximations are possible by truncating the infinite order series to fixed set of coefficients, with the most important terms corresponding to the second order and degree~\cite{scheeres1994}. 
-However, when evaluated close to the body the series expansion will diverge and is no longer accurate. 
+The spherical harmonic expansion is a popular method of representing the gravitational field~\cite{scheeres1996}.
+Approximations are possible by truncating the infinite order series to a fixed set of coefficients, with the most important terms corresponding to the second order and degree~\cite{scheeres1994}. 
+However, when evaluated close to the body, the series expansion will diverge and is not valid inside the circumscribing sphere.
 Therefore, the spherical harmonic representation is not ideal for landing trajectories or those passing close to the surface.
@@
 A polyhedral model of the surface of an asteroid can be determined from remote optical or radar sensors.
-The faces of the polyhedron can be large or small and allow for fine detail such as depression, craters, ridges, or interior voids.
-In addition, there is no requirement for the body to be modeled at a uniformly high resolution so small details can be incorporated with minimal cost.
+The faces of the polyhedron can be large or small and allow for fine detail such as depressions, craters, ridges, or interior voids.
+In addition, there is no requirement for the body to be modeled at a uniformly high resolution, as a result small details can be incorporated with minimal cost.
 From the shape model, an analytical, closed form expression for the gravitational potential can be derived.
@@
 Furthermore, the polyhedron model is an exact solution up to the surface of the body.
-Therefore, this model is ideal for missions traversing large regions both close and far from the asteroid.
+Therefore, this model is ideal for missions traversing large regions of the phase space both close and far from the asteroid.
 
@@
 
-Consider three vectors \( \vecbf{v}_1, \vecbf{v}_2, \vecbf{v}_3 \in \R^{3 \times 1} \), assumed to be ordered in a counterclockwise direction, which define a face.
+Consider three vectors \( \vecbf{v}_1, \vecbf{v}_2, \vecbf{v}_3 \in \R^{3 \times 1} \), assumed to be ordered in a counterclockwise direction about an outward facing normal vector, which define a face.
 It is easy to define the three edges of each face as
@@
 For a periodic orbit, the trajectories will intersect the \Poincare section at two distinct points every half orbit.
-With the addition of a low thrust control input, we are able to expand the reachable set from a distinct point to a larger area on the \Poincare section.
+With the addition of a low thrust control input, we are able to expand the reachable set from a distinct point to a larger region on the \Poincare section.
 \Cref{fig:reachability_set} illustrates this methodology.
@@
 
-The trajectory which minimizes \( d \) is indicated by the red marker in~\cref{fig:poincare_section,fig:phi_distance}.
+The trajectory which minimizes \( d \) is indicated by the red circular markers in~\cref{fig:poincare_section,fig:phi_distance}.
 Since the first reachability set does not include the target we use the minimum state from the first stage to initialize another reachability computation.
@@
 At the same time there is a relatively large difference between the \( \dot{x} \), \( \dot{z} \), and \( z \) components of the forth stage and the target orbit.
-In practice this is not a large concern as we have direct control over the spacecraft velocity via the control input and the equatorial plane still remains within the reachability set of the transfer.
+In practice, this is not a large concern as we have direct control over the spacecraft velocity via the control input and the equatorial plane still remains within the reachability set of the transfer.
 

### 2016-09-22 manuscript.tex
Add some comments from Dr. Lee

@@
 % Motivation for missions/studying asteroids
-Small solar system bodies, such as asteroids and comets, are of significant interest to the scientific community; these small bodies offer great insight into the early formation of the solar system.
+Small solar system bodies, such as asteroids and comets, are of significant interest to the scientific community; These small bodies offer great insight into the early formation of the solar system.
 This insight offers additional detail into the formation of the Earth and also the probable formation of other planetary bodies.
@@
 
-In this analysis, we consider transfers about the asteroid 4769 Castalia.
-Castalia has an accurate shape model and is also considered a potentially hazardous asteroid with a possibility of Earth impact~\cite{hudson1994}.
+In this analysis, we consider orbital transfers about the asteroid 4769 Castalia.
+There is an accurate shape model for Castalia, and it is also considered a potentially hazardous asteroid with a possibility of Earth impact~\cite{hudson1994}.
 We model the gravitational potential field of Castalia using a polyhedron gravity model instead of using a spherical harmonic expansion.
@@
 For indirect optimization, which is based on the calculus of variations, this results in the well-known two-point boundary value problem.
-Insight into the problem or insight by the designer is usually required to determine appropriate initial costates that will converge to the optimal solution and satisfy the desired constraints.
+Insight into the problem is usually required to determine appropriate initial costates that will converge to the optimal solution and satisfy the desired constraints.
 To avoid this issue, we utilize the concept of the reachability set on a lower dimensional \Poincare section.
@@
 
-We define the \Poincare section as the surface normal to \( y = 0 \).
-Following convention, the \Poincare map is defined as the map from one transversal crossing of the surface \( y = 0\) to the next.
-Using the method of Reference~\citenum{scheeres2000}, we remove \( y \) and \( \dot{y} \) from consideration and create a four-dimensional map.
+We apply the \Poincare map with a surface of section chosen to be normal to the position \( y = 0 \).
+The \Poincare map is then defined as the map between successive transversal crossings of the surface of section.
+To ensure a transverse crossing of the section we also require that \( \dot{y} \neq 0 \) when \( y = 0 \).
+With this definition of the \Poincare map, it is possible to remove the two variables \( y \) and \( \dot{y} \) from consideration and create a four-dimensional map from the \Poincare section to itself.
 The \Poincare section, represented by \( \Sigma \), then becomes

### 2017-04-04 setup_repo.sh
Add remote repo locations

@@ -1,9 +1,9 @@
 #!/bin/bash
 
 # add the correct remote repositories
-git_repo="git@github.com:skulumani/2016-AAS-manuscript.git"
-bb_repo="git@bitbucket.org:shankarkulumani/2016_aas_manuscript.git"
-fdcl_repo="git@github.com:fdcl-gwu/2016_AAS_manuscript.git"
+git_repo="git@github.com:skulumani/2017_SSPI_manuscript.git"
+bb_repo="git@bitbucket.org:shankarkulumani/2017_sspi_manuscript.git"
+# fdcl_repo="git@github.com:fdcl-gwu/2016_AAS_manuscript.git"
 
 printf "Setting the origin remote to point to Github, Bitbucket and FDCL:\n\n"
 printf "Github: $git_repo\n"
@@ -11,7 +11,7 @@ printf "Bitbucket: $bb_repo\n"
 printf "FDCL: $fdcl_repo\n\n"
 
 git remote set-url origin --push --add $bb_repo
-git remote set-url origin --push --add $fdcl_repo
+# git remote set-url origin --push --add $fdcl_repo
 git remote set-url origin --push --add $git_repo
 
 printf "Finished! The new remotes are listed.\n"

### 2017-04-04 manuscript.tex
Fix a typo and add the compiled pdf.
Final version for AAS revisions
Use article class and put a fancy tikz image

@@
-\documentclass[]{aiaa-tc}% insert '[draft]' option to show overfull boxes
+\documentclass[]{article}% insert '[draft]' option to show overfull boxes
 
 \usepackage{aiaa_packages}
+\usepackage{tikz_packages}
+\tdplotsetmaincoords{60}{125} % view angle in spherical coordinates
 
@@
  \author{
-  Shankar Kulumani\thanksibid{1}%
-    \thanks{Doctoral Student, \href{mailto:skulumani@gwu.edu}{skulumani@gwu.edu}. Student Member AIAA.}
-  \ and Taeyoung Lee\thanksibid{2}\thanks{Associate Professor, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}.}\\
+  Shankar Kulumani%
+    \thanks{Doctoral Candidate, \href{mailto:skulumani@gwu.edu}{skulumani@gwu.edu}.}
+  \ and Taeyoung Lee\thanks{Associate Professor, \href{mailto:tylee@gwu.edu}{tylee@gwu.edu}.}\\
   {\normalsize\itshape
@@
 
- % Data used by 'handcarry' option if invoked
- \AIAApapernumber{YEAR-NUMBER}
- \AIAAconference{Conference Name, Date, and Location}
- \AIAAcopyright{\AIAAcopyrightD{YEAR}}
-
 \begin{document}
-
 \maketitle
-
 \begin{abstract}\label{sec:abstract}
@@
 Here, we use numerical methods to solve a related optimal control problem, which approximates a single solution that lies on the reachable set.
-\begin{figure}
+\begin{figure}[]
 \centering
-    \begin{scaletikzpicturetowidth}{0.3\textwidth}
-    \begin{tikzpicture}[scale=\tikzscale]
-        \coordinate [label=left:\textcolor{black}{\large \(\vecbf{x}_0\)}] (x0) at (-1,-2);
-        \coordinate [label=below:\textcolor{black}{\large  \(\vecbf{x}_n\)}] (xn) at (1,1);
-        \coordinate [label=left:\textcolor{black}{\large  \(\Sigma\)}] (sigma) at (-4,3);
-        %\coordinate [label=below:\textcolor{black}{\large  \(P(\vec{x})\)}] (P) at (0,-3.5);
-        % define the path of the flow with coordinates
-        \coordinate [label=right:\textcolor{black}{}] (f1) at (5,-2);
-        \coordinate [label=below:\textcolor{black}{\large  \(\psi(t,\vecbf{x}_0)\)}] (f2) at (2,-5);
-        \coordinate [label=right:\textcolor{black}{}] (f3) at (-4,-4);
-        \coordinate [label=right:\textcolor{black}{}] (f4) at (-4,-1);
+\begin{scaletikzpicturetowidth}{0.5\textwidth}
+    \begin{tikzpicture}[tdplot_main_coords,
+          poincare/.style={opacity=.2,very thick,fill=blue},
+          orbit/.style={very thick,black},
+          orbit hidden/.style={very thick,dashed},
+          grid/.style={very thin,black},
+          axis/.style={->,blue,thick},
+          reachability/.style={thick,blue}, scale=\tikzscale]
 
-    %   \draw[help lines] (-10,-10) grid (10,10); %grid
-        \filldraw [black] (x0) circle [radius=3pt];
-        \filldraw [black] (xn) circle [radius=3pt];
+        % nodes for the poincare section
+        \node[label=above:\(\Sigma\)] (upper_right) at (0,5,5) {};
+        \node[] (upper_left) at (0,1,5) {};
+        \node[] (lower_left) at (0,1,0) {};
+        \node[] (lower_right) at (0,5,0) {};
 
-        \draw [ultra thick,black,->-](x0) to[out=20,in=90,distance=2cm] (f1) to[out=-90,in=0,distance=2cm] (f2) to[out=180,in=-45,distance=2cm] (f3) to[out=135,in=-135,distance=2cm] (f4) ;
-        \draw [ultra thick, black,dashed,->] (f4) to[out=45,in=180,distance=1cm] ($(xn)-(2,0)$);
+        % draw poincare section
+        \draw[poincare] (upper_right.center) -- (upper_left.center) -- (lower_left.center) -- (lower_right.center) -- (upper_right.center);
 
-        \draw [ultra thick] plot [smooth cycle, tension=0.1, rotate=5] coordinates { (-4,-3) (4,-3) (4,3) (-4,3) };
+        % draw a periodic orbit
+        \coordinate (center) at (0,0,2);
+        \node[label=below:\(\vecbf{x}_0\)] (x0) at (0,3,2) {};
+        % \node[label=below:\(\vecbf{x}_n\)] at (x0) {};
+        \filldraw (x0) circle (3pt);
 
-        \draw [thick,dashed] (xn) circle [radius=2cm]; % reachability set
+        % \tdplotdrawarc[orbit hidden]{(center)}{3}{90}{200}{}{};
+        \tdplotdrawarc[orbit,<-]{(center)}{3}{-160}{90}{}{};
 
-        \draw [thick,->] (xn) -- ($(xn) + (2.5,0)$);
-        \draw [thick,rotate=45,->] (xn) -- ($(xn) + (2.5,0)$);
-        \draw ($(xn) + (1,0)$) arc [start angle=0,end angle=45, radius=1];
-        \node [draw=none] at (2.4,1.5) {\Large \(\phi_d\)};
-        \draw [decorate,decoration={brace,amplitude=5pt},rotate=45] (xn) -- ($(xn) + (2,0)$);
-        \node [draw=none] at ($ (xn) + (0,1) $) {\Large \( J \)};
+        % draw reachability set on the poincare section
+        \coordinate (reach) at (0,4.5,2);
+        \tdplotsetthetaplanecoords{90}
+
+        \draw[tdplot_rotated_coords,grid] (x0) -- (reach);
+        \draw[tdplot_rotated_coords,grid] (x0) -- ++(-45:1.5);
+
+        \tdplotdrawarc[tdplot_rotated_coords,grid]{(x0)}{0.5}{-45}{90}{above}{\(\phi\)};
+
+        % draw terminal state on reachability set
+        \node[tdplot_rotated_coords,label=above:\(\vecbf{x}_f\)] (xf) at ($ (x0)+(-45:1.5) $) {};
+        \filldraw (xf) circle (3pt);
+
+        \node[tdplot_rotated_coords,label=below:\(J\)] at (xf) {};
+
+        \tdplotdrawarc[tdplot_rotated_coords,reachability]{(x0)}{1.5}{0}{360}{}{};
+        % place
     \end{tikzpicture}
 \end{scaletikzpicturetowidth}
-    \caption{Reachability set on a \Poincare section\label{fig:reachability_set}}
+\caption{Reachability Set\label{fig:reachability_set}}
 \end{figure}
@@
 We use a shooting method to determine the initial costates, \( \vecbf{\lambda}(t_0)\), such that the terminal constraints are satisfied.
-In addition, we implement a multiple shooting method which sub-divides the the entire trajectory into small sub-intervals~\cite{stoer2013}.
+In addition, we implement a multiple shooting method which sub-divides the the entire trajectory into smaller sub-intervals~\cite{stoer2013}.
 The multiple shooting method reduces the sensitivity of the terminal states to the initial conditions.
